### 2020-10-01 paper/paper.Rmd
Add paper JOSS

---
# Example from https://joss.readthedocs.io/en/latest/submitting.html
title: 'ropenblas: Download, Compile and Link OpenBLAS Library with R'
tags:
  - R
  - BLAS
  - Compiling R
  - Compiling OpenBLAS
  - Link OpenBLAS
authors:
  - name: Pedro Rafael Diniz Marinho
    orcid: 0000-0003-1591-8300
    affiliation: 1
affiliations:
 - name: Department of Statistics, Federal University of Paraíba, João Pessoa, Paraíba - PB, Brazil
   index: 1
citation_author: Marinho
date: "`r Sys.Date()`"
year: "`r format(Sys.Date(), '%Y')`"
bibliography: paper.bib
output: rticles::joss_article
header-includes:
  - \usepackage{float}
csl: apa.csl
journal: JOSS
---

# Summary

```{r global_options, include=FALSE}
knitr::opts_chunk$set(fig.pos = 'H')
```

The `ropenblas` package aims to facilitate the daily life of R programmers on GNU/Linux systems without removing the possibility of specifying configurations that they deem convenient. Through the `ropenblas()` and `rcompiler()` functions, the package user will be able to compile and link the R language in his GNU/Linux distribution and link it to the OpenBLAS library, all within R and in a very simple way. All functions work without being influenced by the GNU/Linux distribution and its repositories, that is, it doesn't matter which GNU/Linux distribution is being used. Linking to the OpenBLAS library to R will bring a better computational performance of the language in the most diverse algebraic operations that are commonly used in areas such as statistics, data science and machine learning.

# Introduction

The term "computational efficiency" is very common for those who program statistical methods, in which a large part of them involve algebraic operations that are often reproduced in computationally intensive simulations, such as Monte-Carlo simulations - MC and resampling methods, as is the case with bootstrap resampling. Statistics is just one example within so many other areas that need performance and uses the R language.

In addition to the adoption of good programming practices and the maximum, efficient and adequate use of available computational resources, such as code parallelization, through multicore parallelism procedures allowed by most current processors and operating systems, small adjustments and linkage of libraries can provide useful benefits.

The `ropenblas` package aims to provide useful and simple experiences to R [@R] programmers who develop their activities on GNU/Linux operating systems, these many developers around the world producing codes of great impact for the community. These experiences consist of being able to link any version of the OpenBLAS [@openblas] library to the R language, as well as allowing the programmer to install and link various versions of R and make them available on his operating system as well as switch between these versions as they see fit.

Linking the R language to the OpenBLAS library can bring several benefits to algebraic computing in R. OpenBLAS is an Open-Source implementation of the Basic Linear Algebra Subprograms - BLAS library that is often the first library option for algebraic computing to be linked in the installation of R on many GNU/Linux distributions. The OpenBLAS library is available at <https://github.com/xianyi/OpenBLAS> and adds optimized implementations of linear algebra kernels that can run optimized on various processor architectures. OpenBLAS is based on the GotoBLAS2 project code in version 1.13 [@gotoblas2], code available under the terms of the BSD license.

The functions of the `ropenblas` package can help the R language user to make this link without leaving the R promprt, as well as allowing the user to choose the version of OpenBLAS to be considered, the last stable version being considered by default . Everything is accomplished by functions without many arguments and without major complications to be used. These functions can be very comforting for users of R on GNU/Linux systems who do not feel safe to run several codes in a terminal that runs Shell Script codes for the language configuration.

It is very common to see users of R in distributions with repositories not prone to immediate updates of programs using several tutorials found in communities on the internet suggesting several lines of code and steps that can be potentially dangerous or easy to be misunderstood by many users of R language. Being able to compile, enable resources if necessary and switch between versions of R using simple functions to be used and without leaving the command pompt of the R language is attractive.

# General package information

The `ropenblas` is a package designed to facilitate the linking of the library OpenBLAS with the language R. The package, which works only for Linux systems, will automatically download the latest source code from the OpenBLAS library and compile the code. The package will automatically bind the language R, through the `ropenblas()` function, to use the OpenBLAS library. Everything will be done automatically regardless of the Linux distribution you are using.

The `ropenblas` package is already available on the Comprehensive R Archive Network - CRAN, currently in version 0.2.8 and the project is maintained on GitHub at  <https://github.com/prdm0/ropenblas> where contributors can find others details of the code, information, as well as being able to contribute with the development of the project. Information can also be found on the project website. On the website it is also possible to read the `NEWS.md` file with details of the versions and the focus of the current development. The site is deposited at <https://prdm0.github.io/ropenblas/>. Suggestions for improvements and bug reports can be sent via the link <https://github.com/prdm0/ropenblas/issues>.

```{r logo, echo = FALSE, message = FALSE, fig.cap = "Computer library logo.", fig.align = "center", out.width="30%"}
knitr::include_graphics(path = "logo_ropenblas.png")
```

You can also specify older versions of the OpenBLAS library. Automatically, if no version is specified, the `ropenblas` package will consider the latest version of the library OpenBLAS.

Considering using the OpenBLAS library rather than the BLAS may bring extra optimizations for your code and improved computational performance for your simulations, since OpenBLAS is an optimized implementation of the library BLAS.

Some of the reasons why it is convenient to link R language to the use of BLAS optimized alternatives can be found here. Several other benchmarks that point to improved computing performance by considering the library OpenBLAS can be found on the internet.

The `ropenblas` package, by `rcompiler()` function is also useful if you want to install different versions of the R language. The different versions, specified by the user of the R language, will be compiled and will also be linked to the OpenBLAS library. If you want to switch between compiled versions of the R language, no compilation is needed anymore. This allows you to avoid having to get your hands dirty with tedious operating system settings, regardless of your GNU/Linux distribution. Another great use of the `rcompiler()` function is that you will not be dependent on updating your GNU/Linux distribution repositories and you can always have the latest version of the R language.

The use of the `ropenblas` package will return warnings that help you proceed with the use of the functions. If your internet is not working or if any dependency on the operating system is not present, the package will let you know. Enumerating some advantages of the package:

  1. Everything is done within the R language;
  2. The procedure (use of functions) will be the same for any Linux distribution;
  3. The OpenBLAS library will be compiled and you will choose which build version to bind to R, regardless of your Linux distribution;
  4. The package allows you to install R $\geq 3.1.0$, also allowing you to install one more version, in addition to allowing you to easily switch between those versions;
  5. The linked versions of R will continue to be recognized by their Integrated Development Environment - IDE and nothing will have to be adjusted in your GNU/Linux distribution after using any function of the package;
  6. Unnecessary builds will be avoided. Therefore, if you need to switch between compiled versions of the R language, the use of binaries compiled in previous times will be suggested;
  7. If any errors occur, the functions of the package will not damage the previous installation of the language;
  8. If something better can be done or if a newer version of what you want to install (R or OpenBLAS) exists, the functions will automatically suggest that you consider installing newer versions.

# Dependencies

In addition to dependencies in the form of other packages deposited with CRAN, the `ropenblas` package depends on external dependencies that are normally installed or are easily installed on any GNU/Linux distribution. Are they:

  1. **GNU Make**: GNU Make utility to maintain groups of programs; 
	2. **GNU GCC Compiler (C and Fortran)**: The GNU Compiler Collection - C and Fortran frontends.

These programs that are described in `SystemRequirements` in the package's `DESCRIPTION` file are essential for compiling the OpenBLAS library and the R language. The functions of the `ropenblas` package are designed to identify the lack of these dependencies external to CRAN, informing the package user which dependencies are missing and suggesting that they should be installed. The other dependencies indexed to CRAN are described in `Imports` in the file  `DESCRIPTION`. These will be installed automatically.

Other warnings can also be suggested, such as, for example, a problem with the internet connection. All warnings are given very clearly so that the user has no doubts about the problem that may be occurring.

# Installation

The `ropenblas` package can be installed in two ways. The first is using the `install.packages()` function of the `utils` package which is available in any basic language installation and the second is using the `devtools` package which will allow the package to be installed directly from the development directory on GitHub. All code kept in the master branch of the package project on GitHub can be installed, since there will only be codes that are working properly and ready to use. The two forms of installation follow:

  1. `install.packages("ropenblas")`: for installing the package available at CRAN;
  2. `devtools::install_github(repo = "prdm0/ropenblas, ref = "master", force = TRUE)`: for installing the package from the project development directory on GitHub.

# Exported functions and usage

The `ropenblas` library exports six functions for use which are the `rcompiler()`,  `ropenblas()`,  `last_version_r()`, `last_version_openblas()`, `link_again()` and `rnews()`. All of them are very simple to use and have few arguments that are sufficient to maintain flexibility of use. Any example that follows will consider that the installation of the `ropenblas` package has been carried out and the package has been loaded (`library(ropenblas)`). In addition, functions like `rcompiler()` and `ropenblas()` do not return content or data structures that are of any practical use. What these functions do is configure the GNU/Linux system to use R, configure different versions of the language, switch between versions and link with the OpenBLAS library. It is also possible to obtain a summary of the versions of R and the OpenBLAS library that are available.

The following subsections are intended to explain and exemplify the use of these functions focused on the main problems that can be solved using the `ropenblas` package. Some functions may take a few minutes to run, as they are responsible for compiling code that is considerably larges and complicateds. This is the case with the `rcompiler()` and  `ropenblas()` functions.

## 'last_version_r' function

The function `last_version_r()` automatically searches, in the official repositories of language R, for information about versions of language R. Its general use is  `last_version_r(major = NULL)` , where the argument `major` indicates which is the largest version of R that you want to search for the version list. Therefore, for the argument `major` a number must be passed, preferably an integer that indicates which is the largest version to be considered. Consider the example:

```{r packages, echo=FALSE, cache=TRUE}
library("ropenblas")
```

```{r, prompt=TRUE, dependson="ropenblas", cache=TRUE}
last_version_r(major = 3L)
```

Note that the `last_version_r()` function returns a list of three elements, where the first element called `last_version` returns the latest version of the R language based on the argument `major`. Thus, the latest version of the R language since the largest version is $3$ is version $3.6.3$. The second element of name `versions` of the return list is a vector containing all versions of the language R for `major = 3L`. The third and last element of the return list is named `n` and returns an integer value referring to the number of versions of R given `major = 3L`. By default, the `major` argument of the `last_version_r()` function is `NULL`. Considering the standard, the function will always consider the largest current version of the language, as in the example below:

```{r, dependson="ropenblas", cache=TRUE, prompt=TRUE}
last_version_r(major = NULL)
```

The function is always adapted to search for new versions and will understand the new language updates since it has been implemented in a general way. Therefore, `last_version_r(major = NULL)$last_version` will always return the latest version of R and not the latest version of R available in the repositories of your GNU/Linux distribution. Therefore, it may be that, depending on when this function is performed, different results may occur.

## 'last_version_openblas' function

The `last_version_openblas()` function works similarly to the `last_version_r()` function, returning a list of three elements named in the same way with the information from the latest version, all the versions and the number of versions of the OpenBLAS library, respectively. Unlike the `last_version_r()` function that searches for the versions of R on the official language website, the `last_version_openblas()` function will search for information on the OpenBLAS library versions on official language development repository on GitHub. In addition, due to the way that the versions of the OpenBLAS library are numbered, the function will always consider the universe of all versions of the OpenBLAS library, therefore, being a function without arguments. The latest version of the OpenBLAS library can be returned by doing `last_version_openblas()$last_version`. Just like the `last_version_r()` function, the `last_version_openblas()` function does not depend on which version of OpenBLAS is available in the repositories of your GNU/Linux distribution.

```{r, dependson="ropenblas", cache=TRUE, prompt=TRUE}
last_version_openblas()
```

## 'rcompiler' function

This function is responsible for compiling a version of the R language. The x argument is the version of R that you want to compile. For example, `x = "4.0.2"` will compile and link R-4.0.2 version as the major version on your system. By default (`x = NULL`) will be compiled the latest stable version of the R. For example, to compile the latest stable version of the R language, run `rcompiler()`. The `rcompiler()` function can only be used if the user is an administrator of the GNU/Linux distribution. If the user is using programming IDE's, a screen similar to the image below will be displayed requesting the entry of the system administrator password.

```{r, echo=FALSE, message=FALSE, warning=FALSE, fig.align='center', fig.cap="Window for entering the system administration password.", out.width="55%"}
knitr::include_graphics("root.png")
```

If the user is running the R language in a terminal of the GNU/Linux distribution, a Shell Bash type terminal, they will be asked to include the password by the terminal itself. The function will not change the operation of other programs, nor even major changes will be made in the initial version of R, just summarizing the creation of symbolic links.

The general way of using the function is given by:

**General use**:

```{r, eval=FALSE, prompt=TRUE}
rcompiler(x = NULL, with_blas = NULL, complementary_flags = NULL)
```

The function's arguments are described below:

  - `x`: String with a valid R language version. A list valid of the latest  language versions can be obtained using the `last_version_r()` function. You can move to ``x` any of the returned versions. This is the best way to choose a valid argument for `x`. By default, `x = NULL` is equivalent to pass `last_version_r()$last_version`, that is, it will be considered the last stable version of the R language;
  - `with_blas`: This argument sets the `--with-blas` flag in the R language compilation process and must be passed as a string. Details on the use of this flag can be found here;
  - `complementary_flags`: String with complementary flags to be used in the R language compilation process.

If the goal is to install the R language, switch between versions of R, and link the installed versions of the language with the OpenBLAS library, you shouldn't have to worry about the `with_blas` and `complementary_flags` arguments, respectively. These arguments are useful for a minority of programmers who feel very specific needs to pass complementary flags to be considered in the R language compilation process, inclusion of complementary library directories, among other arguments that can be found in the official language manuals. By default, if nothing is passed to the `with_blas` and `complementary_flags` arguments, the compilation will be performed as follows:

```{bash, eval=FALSE}
./configure --prefix=/opt/R/version_r --enable-memory-profiling 
--enable-R-shlib --enable-threads=posix 
--with-blas="-L/opt/OpenBLAS/lib -I/opt/OpenBLAS/include
-lpthread -lm"
```

As a suggestion and if you want to use the complementary arguments, that is, use `with_blas` and `complementary_flags`, do not change the directory `include` and `lib` of the OpenBLAS library in argument `with_blas`, considering that the `rcompiler()` function will always install the OpenBLAS library in the `/opt/OpenBLAS` directory, thus avoiding problems with breaking important links on your system and in the configuration of the initial version of R. If you try to pass a different installation directory to the OpenBLAS library, the `rcompiler()` function will disregard this installation of OpenBLAS and perform a safe installation in the `/opt/OpenBLAS` directory. Everything is built in this directory and symbolic links are used so that the initial state of R configuration in the GNU/Linux distribution is not changed.  This allows no errors to be made and unforeseen bugs to occur. If there are reasons to consider complementary strings for the arguments `with_blas` and `complementary_flags`, the R language will be compiled as follows:

```{bash, eval=FALSE}
--prefix=/opt/R/version_r --enable-memory-profiling --enable-R-shlib
--enable-threads=posix --with-blas="..." complementary_flags
```

The `rcompiler()` function will also avoid unnecessary compilations. Therefore, if your initial version of R is already linked to some version of the OpenBLAS library, only the R language will be compiled, with no need to compile the OpenBLAS library. Although the initial description of the `rcompiler()` function may seem a little complicated, its use is very simple. Below I will exemplify some situations in which the use of the `rcompiler()` function may be convenient.

**Example**: In the hypothetical situation of an R user on any GNU/Linux distribution, if are interested in knowing the latest version of the R language, installing it and linking it to the OpenBLAS library, it should proceed as follows:

```{r, eval=FALSE, prompt=TRUE}
rcompiler(x = "4.0.2") # or simply rcompiler () or rcompiler (x = NULL)
```

After executing the function, everything will be ready, and can be checked by executing the command `sessionInfo()` in the next execution of R, that is, in a new instance. Briefly, the `sessionInfo()` command will return something like:

```{r, prompt=TRUE}
sessionInfo()
```

Thus the user will know that the compilation of the R library, and if necessary, of the OpenBLAS library was carried out as requested. The user can also use the command `extSoftVersion()["BLAS"]` if it is only necessary to return which version of the OpenBLAS library is being considered, according to the following code:

```{r, prompt=TRUE}
extSoftVersion()["BLAS"]
```

**Example**: In a new hypothetical situation of a user of R having installed two different versions of the R language as presented above, using the function `rcompiler()`, for example, versions 3.6.3 and 4.0.0, so:

```{r, eval=FALSE, prompt=TRUE}
# First installation of R performed by the rcompiler() function:
rcompiler(x = "4.0.0") 
# Second installation of R performed by the rcompiler() function:
rcompiler(x = "3.6.3")
# Returning version 4.0.0 from R:
rcompiler(x = "4.0.0")
```

Running the code `rcompiler(x = "4.0.0")` as the last line of the example above will allow the user to link the binaries previously created in the 4.0.0 compilation process when `rcompiler(x = "4.0.0")` was run for the first time. This will avoid a compilation so that switching between versions of R that have already been compiled will be quick and easy. Although this seems ideal and it is, the function will ask if the user wants to recompile an already compiled version.

**Example**: Assuming that the user of the package has already used the function `rcompiler(x = "4.0.0")` and is in a version other than 4.0.0 but intends to return to version 4.0.0, he can return without compile the language again, as shown in the image below. The output was placed in the form of an image since the return of the functions of the package use symbols that facilitate the user of the functions of the package to understand the suggestions, as well as understand if something went right or wrong.

```{r, eval=FALSE}
rcompiler(x = "4.0.0")
```

```{r, echo=FALSE, message=FALSE, warning=FALSE, fig.align='center', fig.cap="A possible exit from the 'rcompiler' function. Suggestion of switching between versions of R without the need to recompile the language.", out.width="100%"}
knitr::include_graphics("linkar_again.png")
```

Due to the internal dependencies of the `ropenblas` package, it is advisable not to try to go to versions of R prior to 3.1.0, as these dependencies do not work on these versions of R. Therefore, in earlier versions of R, installing the `ropenblas` package will not be possible. Therefore, if the user wishes to return to a more current version of R, he must install the language R in the GNU/Linux distribution without the help of the package. Although it is allowed to install previous versions of R prior to 3.1.0, it will only be done after the user responds to some questions of an alert message, as shown in the image below:

```{r, eval=FALSE, prompt=FALSE}
rcompiler(x = "3.0.0")
```

```{r, echo=FALSE, message=FALSE, warning=FALSE, fig.align='center', fig.cap="Attempted to install an R language version prior to version 3.1.0.", out.width="100%"}
knitr::include_graphics("attention.png")
```

## 'ropenblas' function

The `ropenblas()` function, a function of the same name in the package, links the main version of the R language installed on your operating system with the OpenBLAS library. As in the `rcompiler()` function, the `ropenblas()` function requires the operating system administration password, that is, it must be executed by the system administrator.

Unlike the `rcompiler()` function that will allow multiple versions of R to be available in your GNU/Linux distribution, the `ropenblas()` function will allow only one version of the OpenBLAS library to be installed. The function will allow versions of OpenBLAS $\geq 0.3.0$ to be installed. Even if the function `rcompile()` responsible for compiling and installing the R language has not been used, the function `ropenblas()` may link a version of OpenBLAS to the main installation of R, that is, even if the R is installed by procedures external to the package.

**General use**:

```{r, eval = FALSE, prompt=TRUE}
ropenblas(x = NULL, restart_r = TRUE)
```

The `ropenblas()` function is made up of two arguments. Are they:

  - `x`: String with the version of the OpenBLAS library to be compiled, installed and linked with the main R installation;
  - `restart_r`: Logical value (default `restart_r = TRUE`) to update the R section after compiling, installing and linking the OpenBLAS library.
\end{itemize}

By default, if `x = NULL` the latest version of the OpenBLAS library will be considered. This is equivalent to passing `last_version_openblas()$last_version` to `x`. There are no great reasons to consider an older version of the OpenBLAS library, although the `ropenblas` package will allow this to be done in a simple way, as in the following example:

**Example**: Regardless of how the R language was installed, suppose you want to compile, install and link the latest version of the OpenBLAS library to the R language. This can be done by doing:

```{r, eval=FALSE, prompt=TRUE}
ropenblas()
```

```{r, echo=FALSE, message=FALSE, warning=FALSE, fig.align='center', fig.cap="Output informing the end of the procedure for linking the OpenBLAS library to the R language.", out.width="100%"}
knitr::include_graphics("ropenblas_01.png")
```

**Example**: In situations where the latest version of the OpenBLAS library is already installed, if the user wishes to install a previous version of OpenBLAS, for example the version $0.3.8$, he should make it clear by answering a question, as shown in the image below:

```{r, eval=FALSE, prompt=TRUE}
ropenblas("0.3.8")
```

```{r, echo=FALSE, message=FALSE, warning=FALSE, fig.align='center', fig.cap="Asking if the user really wants to compile and link an older version of the OpenBLAS library.", out.width="100%"}
knitr::include_graphics("ropenblas_02.png")
```

The code below is a small example of the benefits of considering linking the R language to the OpenBLAS library, in which singular-value decomposition of a rectangular matrix is computed, codes that are executed on the same machine, version of R and section. The first part of the code was executed with R without being linked to a version of the OpenBLAS library and the second part was executed after using the `ropenblas()` function. Note that the code when executed in R linked to a version of the OpenBLAS library can be clearly more efficient:

```{r, eval = FALSE}
# Using the BLAS + Lapack library:
# Matrix products: default
# BLAS:   /usr/lib/libblas.so.3.9.0
# LAPACK: /usr/lib/liblapack.so.3.9.0
n <- 1e3L
X <- matrix(rnorm(n * n), n, n)
system.time(svd(X)) 
## user      system      elapsed
## 7.246     0.029       7.286

# ----

# After linking the OpenBLAS library to R using the ropenblas() function:
# Using the OpenBLAS version 0.3.10 library:
# Matrix products: default
# BLAS/LAPACK: /opt/OpenBLAS/lib/libopenblas_haswellp-r0.3.10.so
n <- 1e3L
X <- matrix(rnorm(n * n), n, n)
system.time(svd(X)) 
## user      system    elapsed
## 3.024     2.004     0.677 
```

## 'link_again' function

The `link_again()` function links again the OpenBLAS library with the R language, being useful to correct problems of untying the OpenBLAS library that is common when the operating system is updated.
The function be able to link again the R language with the OpenBLAS library. Thus, `link_again()` will only make the relinkagem when in some previous section of R the `ropenblas()` function has been used for the initial binding of the R language with the OpenBLAS library.

The use of the function is quite simple, just by running the code `link_again()`, since the function has no arguments. It will automatically detect if there was a link break that will be rebuilt again without the need for any compilation. From time to time, after a major update of the operating system, it may be convenient to run the `link_again()` function. Link breakage rarely occurs, but if it does, it can be resolved quickly. The following code and image exemplify a possible reconstruction of symbolic links using the `link_again()` function:

```{r, eval=FALSE, prompt=TRUE}
link_again()
```

```{r, echo=FALSE, message=FALSE, warning=FALSE, fig.align='center', fig.cap="If an unlinking of the OpenBLAS library occurs, the function will re-link the library.", out.width="100%"}
knitr::include_graphics("link_again_01.png")
```

Running the `link_again()` function in a situation where there is no need will not generate problems. The function will return the message that everything is linked correctly, according to the code and image that follows:

```{r, echo=FALSE, message=FALSE, warning=FALSE, fig.align='center', fig.cap="If relinking is not required, the function will make it clear.", out.width="100%"}
knitr::include_graphics("link_again_02.png")
```

## 'rnews function'

Returns the contents of the `NEWS.html` file in the standard browser installed on the operating system. The `NEWS.html` file contains the main changes from the recently released versions of the R language. The goal is to facilitate the query by invoking it directly from the R command prompt. The `rnews()` function is analogous to the news function of the `utils` package. However, using the news command in a terminal style bash shell is possible to receive a message like:

```{r, eval=FALSE}
news()
## starting httpd help server ... done
## Error in browseURL(url): 'browser' must be a non-empty character string
```

If `pdf = FALSE` (default), the `NEWS.html` file will open in the browser, otherwise `NEWS.pdf` will be opened. If `dev = FALSE` (default), it will not show changes made to the language development version. To see changes in the development version, do `dev = TRUE`.

# References

### 2020-10-01 paper/paper.Rmd
Add Statement of Need section

@@
 Linking to the OpenBLAS library to R will bring a better computational performance of the language in the most diverse algebraic operations that are commonly used in areas such as statistics, data science and machine learning.
+
+# Statement of Need
+
+The `ropenblas` package aims to allow algebraic computing of R to be performed using the OpenBLAS library, that is, it allows easy linking of R to the OpenBLAS library on GNU / Linux systems without depending on the distribution repositories.
+This will allow several researches in the areas of statistics, data science and machine learning to take advantage of a more efficient performance in algebraic calculations, for example, multiplication, factorization and matrix inversion.
+The `ropenblas` library, version 0.2.8 will also allow the R programmer to have, in his GNU / Linux distribution, several compiled versions of the R language giving the possibility to easily switch between these versions, this being an Open Source functionality that is only possible in some commercial IDEs of R.
+All this is done within the R language, minimizing the chance of less experienced users to break their operating system by running several instructions that are not perfectly understood.
+
+The fact that the `ropenblas` package does not depend on the repositories of the GNU/Linux distribution will allow that in more stable distributions the R programmer will have at his disposal the most recent version of the OpenBLAS libraries and the R language.
+Everything is done in a safe way, a since the `ropenblas` package uses the stable versions of the official development repositories of the OpenBLAS library and the R programming language, respectively.
+Until the present version, the package has more than 6600 downloads, having an average of more than 820 downloads in the month prior to the date of this submission, based on the official R language repositories.
 

### 2020-10-01 paper/paper.Rmd
update

@@
   - R
-  - BLAS
-  - Compiling R
-  - Compiling OpenBLAS
+  - Compiling R and OpenBLAS
   - Link OpenBLAS
+  - Switch between versions of R
+  - Fast algebraic computing
 authors:
@@
 
-The `ropenblas` package aims to allow algebraic computing of R to be performed using the OpenBLAS library, that is, it allows easy linking of R to the OpenBLAS library on GNU / Linux systems without depending on the distribution repositories.
+The `ropenblas` package aims to allow algebraic computing of R to be performed using the OpenBLAS library, that is, it allows easy linking of R to the OpenBLAS library on GNU/Linux systems without depending on the distribution repositories.
 This will allow several researches in the areas of statistics, data science and machine learning to take advantage of a more efficient performance in algebraic calculations, for example, multiplication, factorization and matrix inversion.
-The `ropenblas` library, version 0.2.8 will also allow the R programmer to have, in his GNU / Linux distribution, several compiled versions of the R language giving the possibility to easily switch between these versions, this being an Open Source functionality that is only possible in some commercial IDEs of R.
+The `ropenblas` library, version 0.2.8 will also allow the R programmer to have, in his GNU/Linux distribution, several compiled versions of the R language giving the possibility to easily switch between these versions, this being an Open Source functionality that is only possible in some commercial IDEs of R.
 All this is done within the R language, minimizing the chance of less experienced users to break their operating system by running several instructions that are not perfectly understood.

### 2020-10-01 paper/paper.Rmd
Reducing the article from 13 to 9 pages

@@
 
-```{r logo, echo = FALSE, message = FALSE, fig.cap = "Computer library logo.", fig.align = "center", out.width="30%"}
-knitr::include_graphics(path = "logo_ropenblas.png")
-```
+<!-- ```{r logo, echo = FALSE, message = FALSE, fig.cap = "Computer library logo.", fig.align = "center", out.width="30%"} -->
+<!-- knitr::include_graphics(path = "logo_ropenblas.png") -->
+<!-- ``` -->
 
@@
 
-These programs that are described in `SystemRequirements` in the package's `DESCRIPTION` file are essential for compiling the OpenBLAS library and the R language.
+<!-- These programs that are described in `SystemRequirements` in the package's `DESCRIPTION` file are essential for compiling the OpenBLAS library and the R language.
 The functions of the `ropenblas` package are designed to identify the lack of these dependencies external to CRAN, informing the package user which dependencies are missing and suggesting that they should be installed.
@@
 These will be installed automatically.
+-->
 
-Other warnings can also be suggested, such as, for example, a problem with the internet connection.
+<!-- Other warnings can also be suggested, such as, for example, a problem with the internet connection.
 All warnings are given very clearly so that the user has no doubts about the problem that may be occurring.
+-->
 
@@
 ```{r, prompt=TRUE, dependson="ropenblas", cache=TRUE}
-last_version_r(major = 3L)
+last_version_r(major = 4L)
 ```
 
-Note that the `last_version_r()` function returns a list of three elements, where the first element called `last_version` returns the latest version of the R language based on the argument `major`.
+<!-- Note that the `last_version_r()` function returns a list of three elements, where the first element called `last_version` returns the latest version of the R language based on the argument `major`.
 Thus, the latest version of the R language since the largest version is $3$ is version $3.6.3$.
@@
 By default, the `major` argument of the `last_version_r()` function is `NULL`.
-Considering the standard, the function will always consider the largest current version of the language, as in the example below:
+-->
 
-```{r, dependson="ropenblas", cache=TRUE, prompt=TRUE}
-last_version_r(major = NULL)
-```
+<!-- Considering the standard, the function will always consider the largest current version of the language, as in the example below: -->
+
+<!-- ```{r, dependson="ropenblas", cache=TRUE, prompt=TRUE} -->
+<!-- last_version_r(major = NULL) -->
+<!-- ``` -->
 
@@
 
-```{r, dependson="ropenblas", cache=TRUE, prompt=TRUE}
-last_version_openblas()
-```
+<!-- ```{r, dependson="ropenblas", cache=TRUE, prompt=TRUE} -->
+<!-- last_version_openblas() -->
+<!-- ``` -->
 
@@
 
-After executing the function, everything will be ready, and can be checked by executing the command `sessionInfo()` in the next execution of R, that is, in a new instance.
-Briefly, the `sessionInfo()` command will return something like:
-
-```{r, prompt=TRUE}
-sessionInfo()
-```
-
+After executing the function, everything will be ready, and can be checked by executing the command `extSoftVersion()["BLAS"]` in the next execution of R, that is, in a new instance.
 Thus the user will know that the compilation of the R library, and if necessary, of the OpenBLAS library was carried out as requested.
-The user can also use the command `extSoftVersion()["BLAS"]` if it is only necessary to return which version of the OpenBLAS library is being considered, according to the following code:
+Briefly, the `extSoftVersion()["BLAS"]` command will return something like:
 
@@
 ```
+
+<!-- ```{r, prompt=TRUE} -->
+<!-- sessionInfo() -->
+<!-- ``` -->
 
@@
 
-**Example**: Assuming that the user of the package has already used the function `rcompiler(x = "4.0.0")` and is in a version other than 4.0.0 but intends to return to version 4.0.0, he can return without compile the language again, as shown in the image below.
+<!-- **Example**: Assuming that the user of the package has already used the function `rcompiler(x = "4.0.0")` and is in a version other than 4.0.0 but intends to return to version 4.0.0, he can return without compile the language again, as shown in the image below.
 The output was placed in the form of an image since the return of the functions of the package use symbols that facilitate the user of the functions of the package to understand the suggestions, as well as understand if something went right or wrong.
+-->
 
-```{r, eval=FALSE}
-rcompiler(x = "4.0.0")
-```
+<!-- ```{r, eval=FALSE} -->
+<!-- rcompiler(x = "4.0.0") -->
+<!-- ``` -->
 
-```{r, echo=FALSE, message=FALSE, warning=FALSE, fig.align='center', fig.cap="A possible exit from the 'rcompiler' function.
-Suggestion of switching between versions of R without the need to recompile the language.", out.width="100%"}
-knitr::include_graphics("linkar_again.png")
-```
+<!-- ```{r, echo=FALSE, message=FALSE, warning=FALSE, fig.align='center', fig.cap="A possible exit from the 'rcompiler' function.
+Suggestion of switching between versions of R without the need to recompile the language.", out.width="100%"} -->
+<!-- knitr::include_graphics("linkar_again.png") -->
+<!-- ``` -->
 
-Due to the internal dependencies of the `ropenblas` package, it is advisable not to try to go to versions of R prior to 3.1.0, as these dependencies do not work on these versions of R.
+<!-- Due to the internal dependencies of the `ropenblas` package, it is advisable not to try to go to versions of R prior to 3.1.0, as these dependencies do not work on these versions of R.
 Therefore, in earlier versions of R, installing the `ropenblas` package will not be possible.
 Therefore, if the user wishes to return to a more current version of R, he must install the language R in the GNU/Linux distribution without the help of the package.
-Although it is allowed to install previous versions of R prior to 3.1.0, it will only be done after the user responds to some questions of an alert message, as shown in the image below:
+Although it is allowed to install previous versions of R prior to 3.1.0, it will only be done after the user responds to some questions of an alert message, as shown in the image below: -->
 
-```{r, eval=FALSE, prompt=FALSE}
-rcompiler(x = "3.0.0")
-```
+<!-- ```{r, eval=FALSE, prompt=FALSE} -->
+<!-- rcompiler(x = "3.0.0") -->
+<!-- ``` -->
 
-```{r, echo=FALSE, message=FALSE, warning=FALSE, fig.align='center', fig.cap="Attempted to install an R language version prior to version 3.1.0.", out.width="100%"}
-knitr::include_graphics("attention.png")
-```
+<!-- ```{r, echo=FALSE, message=FALSE, warning=FALSE, fig.align='center', fig.cap="Attempted to install an R language version prior to version 3.1.0.", out.width="100%"} -->
+<!-- knitr::include_graphics("attention.png") -->
+<!-- ``` -->
 
@@
 
-The code below is a small example of the benefits of considering linking the R language to the OpenBLAS library, in which singular-value decomposition of a rectangular matrix is computed, codes that are executed on the same machine, version of R and section.
+<!-- The code below is a small example of the benefits of considering linking the R language to the OpenBLAS library, in which singular-value decomposition of a rectangular matrix is computed, codes that are executed on the same machine, version of R and section.
 The first part of the code was executed with R without being linked to a version of the OpenBLAS library and the second part was executed after using the `ropenblas()` function.
-Note that the code when executed in R linked to a version of the OpenBLAS library can be clearly more efficient:
+Note that the code when executed in R linked to a version of the OpenBLAS library can be clearly more efficient: -->
 
-```{r, eval = FALSE}
-# Using the BLAS + Lapack library:
-# Matrix products: default
-# BLAS:   /usr/lib/libblas.so.3.9.0
-# LAPACK: /usr/lib/liblapack.so.3.9.0
-n <- 1e3L
-X <- matrix(rnorm(n * n), n, n)
-system.time(svd(X)) 
-## user      system      elapsed
-## 7.246     0.029       7.286
+<!-- ```{r, eval = FALSE} -->
+<!-- # Using the BLAS + Lapack library: -->
+<!-- # Matrix products: default -->
+<!-- # BLAS:   /usr/lib/libblas.so.3.9.0 -->
+<!-- # LAPACK: /usr/lib/liblapack.so.3.9.0 -->
+<!-- n <- 1e3L -->
+<!-- X <- matrix(rnorm(n * n), n, n) -->
+<!-- system.time(svd(X))  -->
+<!-- ## user      system      elapsed -->
+<!-- ## 7.246     0.029       7.286  -->
 
-# ----
+<!-- # ---- -->
 
-# After linking the OpenBLAS library to R using the ropenblas() function:
-# Using the OpenBLAS version 0.3.10 library:
-# Matrix products: default
-# BLAS/LAPACK: /opt/OpenBLAS/lib/libopenblas_haswellp-r0.3.10.so
-n <- 1e3L
-X <- matrix(rnorm(n * n), n, n)
-system.time(svd(X)) 
-## user      system    elapsed
-## 3.024     2.004     0.677 
-```
+<!-- # After linking the OpenBLAS library to R using the ropenblas() function: -->
+<!-- # Using the OpenBLAS version 0.3.10 library: -->
+<!-- # Matrix products: default -->
+<!-- # BLAS/LAPACK: /opt/OpenBLAS/lib/libopenblas_haswellp-r0.3.10.so -->
+<!-- n <- 1e3L -->
+<!-- X <- matrix(rnorm(n * n), n, n) -->
+<!-- system.time(svd(X))  -->
+<!-- ## user      system    elapsed -->
+<!-- ## 3.024     2.004     0.677  -->
+<!-- ``` -->
 
@@
 
-Running the `link_again()` function in a situation where there is no need will not generate problems.
-The function will return the message that everything is linked correctly, according to the code and image that follows:
+<!-- Running the `link_again()` function in a situation where there is no need will not generate problems.
+The function will return the message that everything is linked correctly, according to the code and image that follows: -->
 
-```{r, echo=FALSE, message=FALSE, warning=FALSE, fig.align='center', fig.cap="If relinking is not required, the function will make it clear.", out.width="100%"}
-knitr::include_graphics("link_again_02.png")
-```
+<!-- ```{r, echo=FALSE, message=FALSE, warning=FALSE, fig.align='center', fig.cap="If relinking is not required, the function will make it clear.", out.width="100%"} -->
+<!-- knitr::include_graphics("link_again_02.png") -->
+<!-- ``` -->
 

### 2020-12-10 README.Rmd
Update README.md

---
title: "Download, Compile and Link OpenBLAS Library with R"
author: |
  | **Author**: Prof. Dr. Pedro Rafael Diniz Marinho
  | **Package website**: **<https://prdm0.github.io/ropenblas>**
  |
  |
  |
  | **Summary**
output: 
  bookdown::github_document2:
    toc: true
toccolor: 'blue'
---

[![last](https://www.r-pkg.org/badges/last-release/ropenblas)](https://CRAN.R-project.org/package=ropenblas)
[![CRAN_Status_Badge](https://www.r-pkg.org/badges/version/ropenblas)](https://CRAN.R-project.org/package=ropenblas)
[![total](http://cranlogs.r-pkg.org/badges/grand-total/ropenblas)](https://CRAN.R-project.org/package=ropenblas)
[![month](https://cranlogs.r-pkg.org/badges/ropenblas)](https://CRAN.R-project.org/package=ropenblas)

<img src="https://raw.githubusercontent.com/prdm0/ropenblas/master/logo.png" height="270" width="250" align="right" />

# General aspects

The [**ropenblas**](https://prdm0.github.io/ropenblas/) is a package designed to facilitate the linking of the library [**OpenBLAS**](https://www.openblas.net/) with the language [**R**](https://www.r-project.org/). The package, which works only for Linux systems, will automatically download the latest source code from the [**OpenBLAS**](https://www.openblas.net/) library and compile the code. The package will automatically bind the language [**R**](https://www.r-project.org/), through the `ropenblas()` function, to use the [**OpenBLAS**](https://www.openblas.net/) library. Everything will be done automatically regardless of the Linux distribution you are using.

You can also specify older versions of the [**OpenBLAS**](https://www.openblas.net/) library. Automatically, if no version is specified, the [**ropenblas**](https://prdm0.github.io/ropenblas/) package will consider the latest version of the library [**OpenBLAS**](https://www.openblas.net/).

Considering using the [**OpenBLAS**](https://www.openblas.net/) library rather than the [**BLAS**](http://www.netlib.org/blas/) may bring extra optimizations for your code and improved computational performance for your simulations, since [**OpenBLAS**](https://www.openblas.net/) is an optimized implementation of the library [**BLAS**](http://www.netlib.org/blas/).

Some of the reasons why it is convenient to link [**R**](https://www.r-project.org/) language to the use of [**BLAS**](http://www.netlib.org/blas/) optimized alternatives can be found [**here**](https://csantill.github.io/RPerformanceWBLAS/). Several other [**benchmarks**](https://en.wikipedia.org/wiki/Benchmarking) that point to improved computing performance by considering the library [**OpenBLAS**](https://www.openblas.net/) can be found on the internet.

The ropenblas package, by `rcompiler()` function is also useful if you want to install different versions of the [**R**](https://www.r-project.org/) language. The different versions, specified by the user of the [**R**](https://www.r-project.org/) language, will be compiled and will also be linked to the [**OpenBLAS**](https://www.openblas.net/) library. If you want to switch between compiled versions of the [**R**](https://www.r-project.org/) language, no compilation is needed anymore. This allows you to avoid having to get your hands dirty with tedious operating system settings, regardless of your GNU/Linux distribution. Another great use of the `rcompiler()` function is that you will not be dependent on updating your GNU/Linux distribution repositories and you can always have the latest version of the [**R**](https://www.r-project.org/) language.

The use of the ropenblas package will return warnings that help you proceed with the use of the functions. If your internet is not working or if any dependency on the operating system is not present, the package will let you know.

# Dependencies

You must install the following dependencies on your operating system (Linux):

   1 - **GNU Make**: GNU Make utility to maintain groups of programs; <br/>

   2 - **GNU GCC Compiler (C and Fortran)**: The GNU Compiler Collection - C and Fortran frontends.

Do not worry that you will be notified if any of these dependencies are not installed.

# Installation

Installing the [**ropenblas**](https://prdm0.github.io/ropenblas/) library is easy and will require you to have installed the **devtools** package. This will allow you to install the [**ropenblas**](https://prdm0.github.io/ropenblas/) package directly from GitHub. To install, after installing the **devtools** package, do:

```
devtools::install_github(repo = "prdm0/ropenblas", force = TRUE)
```

or

```
install.packages("ropenblas")
```

**Note**: If you want to access the latest features of the [**ropenblas**](https://prdm0.github.io/ropenblas/) package, install it using the first procedure.

# Use

The [**ropenblas**](https://prdm0.github.io/ropenblas/) package currently provides five functions: `ropenblas()`, `rcompiler()`, `last_version_openblas()`, `last_version_r()` and `link_again()`. First of all, do:

```
library(ropenblas)
```

## 'ropenblas' function:

Installing, compiling, and linking the [**OpenBLAS**](https://www.openblas.net/) version **0.3.12** library to the [**R**](https://www.r-project.org/) language:

```
ropenblas(x = "0.3.12")
```

**Notes**:

   - You do not have to in every section of [**R**](https://www.r-project.org/) make use of the `ropenblas()` function. Once the function is used, [**R**](https://www.r-project.org/) will always consider using the [**OpenBLAS**](https://www.openblas.net/) library in future sections.

   - [**OpenBLAS**](https://www.openblas.net/) versions tested: 0.3.0, 0.3.1, 0.3.2, 0.3.3, 0.3.4, 0.3.5, 0.3.6, 0.3.7, 0.3.8, 0.3.9, 0.3.10, 0.3.11 and 0.3.12. These are the values that will be passed to `x` in `ropenblas(x)`;

   - If `x = NULL`, the latest stable version of the [**OpenBLAS**](https://www.openblas.net/) library will be compiled and linked to [**R**](https://www.r-project.org/).

### Details

Your linux operating system may already be configured to use the [**OpenBLAS**](https://www.openblas.net/) library. Therefore, most likely [**R**](https://www.r-project.org/) will already be linked to this library. To find out if the [**R**](https://www.r-project.org/) language is using the [**OpenBLAS**](https://www.openblas.net/) library, at [**R**](https://www.r-project.org/), do:

```
extSoftVersion()["BLAS"]
```

If [**R**](https://www.r-project.org/) is using the [**OpenBLAS**](https://www.openblas.net/) library, something like `/any_directory/libopenblas.so` should be returned. Therefore, there should be the name **openblas** in the **s**hared **o**bject returned (file extension **.so**).

If the `ropenblas()` function can identify that the [**R**](https://www.r-project.org/) language is using the version of [**OpenBLAS**](https://www.openblas.net/) you wish to configure, a warning message will be returned asking if you really would like to proceed with the configuration again.

The `ropenblas()` function will download the desired version of the library [**OpenBLAS**](https://www.openblas.net/), compile and install the library in the `/opt` directory of your operational system. If the directory does not exist, it will be created so that the installation can be completed. Subsequently, files from the version of [**BLAS**](http://www.netlib.org/blas/) used in [**R**](https://www.r-project.org/) will be symbolically linked to the shared object files of the library version [**OpenBLAS**](https://www.openblas.net/) compiled and installed in `/opt`.

You must be the operating system administrator to use this library. Therefore, do not attempt to use it without telling your system administrator. If you have the ROOT password, you will be responsible for everything you do on your operating system.

You will not necessarily have to run `ropenblas()` on every section of [**R**](https://www.r-project.org/). Almost always it will not be necessary. However, it may be that the [**R**](https://www.r-project.org/) is updated by the operating system (GNU/Linux). Thus, it may be that in this update the [**R**](https://www.r-project.org/) unlink with the [**OpenBLAS**](https://www.openblas.net/) library. Therefore, from time to time check using the command `extSoftVersion()["BLAS"]` if the link with [**OpenBLAS**](https://www.openblas.net/) is correct, otherwise run the command `ropenblas()` again.

## 'last_version_r' function:

Given the higher version, the function will return the latest stable version of the [**R**](https://www.r-project.org/) language. See the following example:

```
> last_version_r()
$last_version
[1] "4.0.3"

$versions
[1] "4.0.0" "4.0.1" "4.0.2" "4.0.3"

$n
[1] 4
```

or

```
> last_version_r(major = 3L)
$last_version
[1] "3.6.3"

$versions
 [1] "3.0.0"         "3.0.1"         "3.0.2"         "3.0.3"         "3.1.0"         "3.1.1"         "3.1.2"         "3.1.3"        
 [9] "3.2.0"         "3.2.1"         "3.2.2"         "3.2.3"         "3.2.4-revised" "3.2.4"         "3.2.5"         "3.3.0"        
[17] "3.3.1"         "3.3.2"         "3.3.3"         "3.4.0"         "3.4.1"         "3.4.2"         "3.4.3"         "3.4.4"        
[25] "3.5.0"         "3.5.1"         "3.5.2"         "3.5.3"         "3.6.0"         "3.6.1"         "3.6.2"         "3.6.3"

$n
[1] 32
```

**Note**: If `major = NULL`, the function will consider the major release number.

## 'last_version_openblas' function:

The `last_version_openblas()` function automatically searches [**OpenBLAS**](https://www.openblas.net/) library versions in the official [**GitHub**](https://github.com/xianyi/OpenBLAS) project.

```
> last_version_openblas()
$last_version
[1] "0.3.12"

$versions
 [1] "0.1alpha1"   "0.1alpha2"   "0.1alpha2.1" "0.1alpha2.2" "0.1alpha2.3" "0.1alpha2.4" "0.1alpha2.5" "0.1.0"      
 [9] "0.1.1"       "0.2.0"       "0.2.1"       "0.2.2"       "0.2.3"       "0.2.4"       "0.2.5"       "0.2.6"      
[17] "0.2.7"       "0.2.8"       "0.2.9"       "0.2.9.rc1"   "0.2.9.rc2"   "0.2.10"      "0.2.10.rc1"  "0.2.10.rc2" 
[25] "0.2.11"      "0.2.12"      "0.2.13"      "0.2.14"      "0.2.15"      "0.2.16"      "0.2.16.rc1"  "0.2.17"     
[33] "0.2.18"      "0.2.19"      "0.2.20"      "0.3.0"       "0.3.1"       "0.3.2"       "0.3.3"       "0.3.4"      
[41] "0.3.5"       "0.3.6"       "0.3.7"       "0.3.8"       "0.3.9"       "0.3.10"      "0.3.11"      "0.3.12"

$n
[1] 48
```

## 'rcompiler' function:

This function is responsible for compiling a version of the [**R**](https://www.r-project.org/) language. The `x` argument is the version of [**R**](https://www.r-project.org/) that you want to compile. For example, `x = "4.0.0"` will compile and link **R-4.0.0** version as the major version on your system. By default (`x = NULL`) will be compiled the latest stable version of the [**R**](https://www.r-project.org/).

For example, to compile the latest stable version of the [**R**](https://www.r-project.org/) language, do:

```
rcompiler()
```

Regardless of your GNU/Linux distribution and what version of [**R**](https://www.r-project.org/) is in your repositories, you can have the latest stable version of the [**R**](https://www.r-project.org/) language compiled into your computer architecture.

You can use the `rcompiler()` function to compile different versions of [**R**](https://www.r-project.org/). For example, running `rcompiler(x = "3.6.3")` and `rcompiler()` will install versions 3.6.3 and 4.0.0 on its GNU/Linux distribution, respectively. If you are in version 4.0.0 of [**R**](https://www.r-project.org/) and run the code `rcompiler(x = "3.6.3")` again, the function will identify the existence of version 3.6.3 in the system and give you the option to use the binaries that were built in a previous compilation. This avoids unnecessarys compilations.

In addition to the `x` argument, the` rcompiler()` function has two other arguments that will allow you to change and pass new compilation flags. Are they:

1. `with_blas`: This argument sets the `--with-blas` flag in the R language compilation process and must be passed as a string. Details on the use of this flag can be found [**here**](https://cran.r-project.org/doc/manuals/r-devel/R-admin.html). If `with_blas = NULL` (default), then it will be considered:

   ```
   ./configure --prefix=/opt/R/version_r --enable-memory-profiling --enable-R-shlib --enable-threads=posix
   --with-blas="-L/opt/OpenBLAS/lib -I/opt/OpenBLAS/include -lpthread -lm"
   ```

   Most likely, you will have little reason to change this argument. Unless you know what you're doing, consider `with_blas = NULL`. Do not change the installation directory, that is, always consider `--prefix = /opt/R/version_r`, where` version_r` is a valid version of [**R**](https://www.r-project.org/). For a list of valid versions of [**R**](https://www.r-project.org/), run the `last_version_r()`.
Installing [**R**](https://www.r-project.org/) in the `/opt/R/version_r` directory is important because some functions in the package require this. Both the [**R**](https://www.r-project.org/) language and the [**OpenBLAS**](https://www.openblas.net/) library will be installed in the `/opt` directory. If this directory does not exist in your GNU/Linux distribution, it will be created;

2. `complementary_flags`: String (`complementary_flags = NULL` by default) for adding complementary flags in the [**R**](https://www.r-project.org/) language compilation process. Passing a string to `complementary_flags` will compile it in the form:

   ```
    ./configure --with-blas="..." complementary_flags
   ```

## 'link_again' function:

The `link_again` function links again the [**OpenBLAS**](https://www.openblas.net/) library with the [**R**](https://www.r-project.org/) language, being useful to correct problems of untying the [**OpenBLAS**](https://www.openblas.net/) library that is common when the operating system is updated.

The function `link_again` be able to link again the [**R**](https://www.r-project.org/) language with the [**OpenBLAS**](https://www.openblas.net/) library. Thus, link_again will only make the relinkagem when in some previous section of
[**R**](https://www.r-project.org/) the ropenblas function has been used for the initial binding of the [**R**](https://www.r-project.org/) language with the [**OpenBLAS**](https://www.openblas.net/) library.

For example, to relink the [**OpenBLAS**](https://www.openblas.net/) library with the [**R**](https://www.r-project.org/) language, do:

```
link_again()
```

If `restart_r = TRUE` (default), a new section of [**R**](https://www.r-project.org/) is started after linking the [**OpenBLAS**](https://www.openblas.net/) library.

In situations where there was a disconnection due to an update of the operating system, the `ropenblas` function can be used to
relink the [**OpenBLAS**](https://www.openblas.net/) library with the [**R**](https://www.r-project.org/) language, however, it will be necessary to compile the [**OpenBLAS**](https://www.openblas.net/) library again. If you are interested in recompiling the
[**OpenBLAS**](https://www.openblas.net/) library and linking with [**R**](https://www.r-project.org/), use the `ropenblas` function. If the interest is to take advantage of a previous compilation of the [**OpenBLAS**](https://www.openblas.net/) library, the
function `link_again` may be useful.

## 'rnews' function:

Returns the contents of the [**NEWS.html**](https://cran.r-project.org/doc/manuals/r-release/NEWS.html) file in the standard browser installed on the operating system. The [**NEWS.html**](https://cran.r-project.org/doc/manuals/r-release/NEWS.html) file contains the main changes from the recently released versions of the [**R**](https://www.r-project.org/) language. The goal is to facilitate the query by invoking it directly from the [**R**](https://www.r-project.org/) command prompt. The rnews function is analogous to the news function of the utils package. However, using the news command in a terminal style bash shell is possible to receive a message like:

```
> news()
starting httpd help server ... done
Error in browseURL(url) : 'browser' must be a non-empty character string
```

If `pdf = FALSE` (default), the [**NEWS.html**](https://cran.r-project.org/doc/manuals/r-release/NEWS.html) file will open in the browser, otherwise [**NEWS.pdf**](https://cran.r-project.org/doc/manuals/r-release/NEWS.pdf) will be opened. If `dev = FALSE` (default), it will not show changes made to the language development version. To see changes in the development version, do `dev = TRUE`.

# Advantages of using ropenblas package:

Some advantages of using the [**ropenblas**](https://prdm0.github.io/ropenblas/) library:

   - Everything is done within the [**R**](https://www.r-project.org/) language;

   - The procedure will be the same for any Linux distribution;

   - The [**OpenBLAS**](https://www.openblas.net/) library will be compiled and you will choose which build version to bind to [**R**](https://www.r-project.org/), regardless of your Linux distribution;

   - If your GNU/Linux distribution does not have updated versions of [**OpenBLAS**](https://www.openblas.net/), it matters little. The ropenblas package fetches the latest stable release of the [**OpenBLAS**](https://www.openblas.net/) library development account on GitHub;

   - You do not need to know Linux well. In some distributions, it may not be so simple for a less experienced user to compile and link the library to the [**OpenBLAS**](https://www.openblas.net/) library with the [**R**](https://www.r-project.org/) language;

   - It is much easier to direct a person to link [**OpenBLAS**](https://www.openblas.net/) with [**R**](https://www.r-project.org/) saying "run `ropenblas()` within [**R**](https://www.r-project.org/)" than asking that person to verify that an unoptimized version of [**BLAS**](http://www.netlib.org/blas/) installed on the system. Then you have to guide the removal of the unoptimized version of [**BLAS**](http://www.netlib.org/blas/) and guide it to the installation of the library [**OpenBLAS**](https://www.openblas.net/) through the most diverse procedures depending on the GNU/Linux distribution used;

   - As stated earlier, the procedure works for any Linux and this includes Android. If your Android is capable of running privileged commands (ROOT) and if you have [**R**](https://www.r-project.org/) installed via Termux with the required dependencies, you can compile and link [**OpenBLAS**](https://www.openblas.net/) with [**R**](https://www.r-project.org/) using ropenblas;

   - With the `rcompiler()` function you can build any version of [**R**](https://www.r-project.org/) into your computer architecture, which includes the most stable version of the language;

   - What is the latest stable version of [**R**](https://www.r-project.org/)? Are you too lazy to go to the [**R**](https://www.r-project.org/) site? Run `ropenblas::last_version_r(major = NULL)`.

### 2020-12-10 README.Rmd
Update README.md file.

@@
   bookdown::github_document2:
+    number_sections: true
     toc: true
+    toc_depth: 2
 toccolor: 'blue'

### 2020-12-11 README.Rmd
Update README.md

--- 2020-12-10 README.Rmd
@@
 author: |
-  | **Author**: Prof. Dr. Pedro Rafael Diniz Marinho
   | **Package website**: **<https://prdm0.github.io/ropenblas>**
@@
 If your internet is not working or if any dependency on the operating system is not present, the package will let you know.
+
+# Advantages of using ropenblas package
+
+Some advantages of using the [**ropenblas**](https://prdm0.github.io/ropenblas/) library:
+
+   - Everything is done within the [**R**](https://www.r-project.org/) language;
+
+   - The procedure will be the same for any Linux distribution;
+
+   - The [**OpenBLAS**](https://www.openblas.net/) library will be compiled and you will choose which build version to bind to [**R**](https://www.r-project.org/), regardless of your Linux distribution;
+
+   - If your GNU/Linux distribution does not have updated versions of [**OpenBLAS**](https://www.openblas.net/), it matters little.
+The ropenblas package fetches the latest stable release of the [**OpenBLAS**](https://www.openblas.net/) library development account on GitHub;
+
+   - You do not need to know Linux well.
+In some distributions, it may not be so simple for a less experienced user to compile and link the library to the [**OpenBLAS**](https://www.openblas.net/) library with the [**R**](https://www.r-project.org/) language;
+
+   - It is much easier to direct a person to link [**OpenBLAS**](https://www.openblas.net/) with [**R**](https://www.r-project.org/) saying "run `ropenblas()` within [**R**](https://www.r-project.org/)" than asking that person to verify that an unoptimized version of [**BLAS**](http://www.netlib.org/blas/) installed on the system.
+Then you have to guide the removal of the unoptimized version of [**BLAS**](http://www.netlib.org/blas/) and guide it to the installation of the library [**OpenBLAS**](https://www.openblas.net/) through the most diverse procedures depending on the GNU/Linux distribution used;
+
+   - As stated earlier, the procedure works for any Linux and this includes Android.
+If your Android is capable of running privileged commands (ROOT) and if you have [**R**](https://www.r-project.org/) installed via Termux with the required dependencies, you can compile and link [**OpenBLAS**](https://www.openblas.net/) with [**R**](https://www.r-project.org/) using ropenblas;
+
+   - With the `rcompiler()` function you can build any version of [**R**](https://www.r-project.org/) into your computer architecture, which includes the most stable version of the language;
+
+   - What is the latest stable version of [**R**](https://www.r-project.org/)? Are you too lazy to go to the [**R**](https://www.r-project.org/) site? Run `ropenblas::last_version_r(major = NULL)`.
 
@@
 
-## 'ropenblas' function:
+## 'ropenblas' function
 
@@
 
-### Details
+**Details**
 
@@
 
-## 'last_version_r' function:
+## 'last_version_r' function
 
@@
 
-## 'last_version_openblas' function:
+## 'last_version_openblas' function
 
@@
 
-## 'rcompiler' function:
+## 'rcompiler' function
 
@@
 
-## 'link_again' function:
+## 'link_again' function
 
@@
 
-## 'rnews' function:
+## 'rnews' function
 
@@
 To see changes in the development version, do `dev = TRUE`.
-
-# Advantages of using ropenblas package:
-
-Some advantages of using the [**ropenblas**](https://prdm0.github.io/ropenblas/) library:
-
-   - Everything is done within the [**R**](https://www.r-project.org/) language;
-
-   - The procedure will be the same for any Linux distribution;
-
-   - The [**OpenBLAS**](https://www.openblas.net/) library will be compiled and you will choose which build version to bind to [**R**](https://www.r-project.org/), regardless of your Linux distribution;
-
-   - If your GNU/Linux distribution does not have updated versions of [**OpenBLAS**](https://www.openblas.net/), it matters little.
-The ropenblas package fetches the latest stable release of the [**OpenBLAS**](https://www.openblas.net/) library development account on GitHub;
-
-   - You do not need to know Linux well.
-In some distributions, it may not be so simple for a less experienced user to compile and link the library to the [**OpenBLAS**](https://www.openblas.net/) library with the [**R**](https://www.r-project.org/) language;
-
-   - It is much easier to direct a person to link [**OpenBLAS**](https://www.openblas.net/) with [**R**](https://www.r-project.org/) saying "run `ropenblas()` within [**R**](https://www.r-project.org/)" than asking that person to verify that an unoptimized version of [**BLAS**](http://www.netlib.org/blas/) installed on the system.
-Then you have to guide the removal of the unoptimized version of [**BLAS**](http://www.netlib.org/blas/) and guide it to the installation of the library [**OpenBLAS**](https://www.openblas.net/) through the most diverse procedures depending on the GNU/Linux distribution used;
-
-   - As stated earlier, the procedure works for any Linux and this includes Android.
-If your Android is capable of running privileged commands (ROOT) and if you have [**R**](https://www.r-project.org/) installed via Termux with the required dependencies, you can compile and link [**OpenBLAS**](https://www.openblas.net/) with [**R**](https://www.r-project.org/) using ropenblas;
-
-   - With the `rcompiler()` function you can build any version of [**R**](https://www.r-project.org/) into your computer architecture, which includes the most stable version of the language;
-
-   - What is the latest stable version of [**R**](https://www.r-project.org/)? Are you too lazy to go to the [**R**](https://www.r-project.org/) site? Run `ropenblas::last_version_r(major = NULL)`.

### 2020-12-15 README.Rmd
Update README.md.
Update README.md. Adding animated examples via the asciicast package. Updating site.

@@
 
-   - As stated earlier, the procedure works for any Linux and this includes Android.
-If your Android is capable of running privileged commands (ROOT) and if you have [**R**](https://www.r-project.org/) installed via Termux with the required dependencies, you can compile and link [**OpenBLAS**](https://www.openblas.net/) with [**R**](https://www.r-project.org/) using ropenblas;
+   <!-- - As stated earlier, the procedure works for any Linux and this includes Android.
+If your Android is capable of running privileged commands (ROOT) and if you have [**R**](https://www.r-project.org/) installed via Termux with the required dependencies, you can compile and link [**OpenBLAS**](https://www.openblas.net/) with [**R**](https://www.r-project.org/) using ropenblas; -->
 
@@
 ```
-devtools::install_github(repo = "prdm0/ropenblas", force = TRUE)
+remotes::install_github(repo = "prdm0/ropenblas", force = TRUE)
 ```
@@
 
-**Note**: If you want to access the latest features of the [**ropenblas**](https://prdm0.github.io/ropenblas/) package, install it using the first procedure.
+<!-- **Note**: If you want to access the latest features of the [**ropenblas**](https://prdm0.github.io/ropenblas/) package, install it using the first procedure. -->
 
@@
 
-Installing, compiling, and linking the [**OpenBLAS**](https://www.openblas.net/) version **0.3.12** library to the [**R**](https://www.r-project.org/) language:
+Installing, compiling, and linking the [**OpenBLAS**](https://www.openblas.net/) version **0.3.13** library to the [**R**](https://www.r-project.org/) language:
 
-```
-ropenblas(x = "0.3.12")
+```{r, fig.align='center',  echo=FALSE}
+knitr::include_graphics(path = "inst/asciicast/ropenblas.svg")
 ```
 
-**Notes**:
+<!-- **Notes**:  -->
 
-   - You do not have to in every section of [**R**](https://www.r-project.org/) make use of the `ropenblas()` function.
+<!--    - You do not have to in every section of [**R**](https://www.r-project.org/) make use of the `ropenblas()` function.
 Once the function is used, [**R**](https://www.r-project.org/) will always consider using the [**OpenBLAS**](https://www.openblas.net/) library in future sections.
+-->
 
-   - [**OpenBLAS**](https://www.openblas.net/) versions tested: 0.3.0, 0.3.1, 0.3.2, 0.3.3, 0.3.4, 0.3.5, 0.3.6, 0.3.7, 0.3.8, 0.3.9, 0.3.10, 0.3.11 and 0.3.12.
-These are the values that will be passed to `x` in `ropenblas(x)`;
+<!--    - [**OpenBLAS**](https://www.openblas.net/) versions tested: 0.3.0, 0.3.1, 0.3.2, 0.3.3, 0.3.4, 0.3.5, 0.3.6, 0.3.7, 0.3.8, 0.3.9, 0.3.10, 0.3.11, 0.3.12 and 0.3.13.
+These are the values that will be passed to `x` in `ropenblas(x)`;  -->
 
-   - If `x = NULL`, the latest stable version of the [**OpenBLAS**](https://www.openblas.net/) library will be compiled and linked to [**R**](https://www.r-project.org/).
+<!--    - If `x = NULL`, the latest stable version of the [**OpenBLAS**](https://www.openblas.net/) library will be compiled and linked to [**R**](https://www.r-project.org/). -->
 
-**Details**
+<!-- **Details** -->
 
-Your linux operating system may already be configured to use the [**OpenBLAS**](https://www.openblas.net/) library.
+<!-- Your linux operating system may already be configured to use the [**OpenBLAS**](https://www.openblas.net/) library.
 Therefore, most likely [**R**](https://www.r-project.org/) will already be linked to this library.
-To find out if the [**R**](https://www.r-project.org/) language is using the [**OpenBLAS**](https://www.openblas.net/) library, at [**R**](https://www.r-project.org/), do:
+To find out if the [**R**](https://www.r-project.org/) language is using the [**OpenBLAS**](https://www.openblas.net/) library, at [**R**](https://www.r-project.org/), do: -->
 
-```
-extSoftVersion()["BLAS"]
-```
+<!-- ``` -->
+<!-- extSoftVersion()["BLAS"] -->
+<!-- ``` -->
 
-If [**R**](https://www.r-project.org/) is using the [**OpenBLAS**](https://www.openblas.net/) library, something like `/any_directory/libopenblas.so` should be returned.
+<!-- If [**R**](https://www.r-project.org/) is using the [**OpenBLAS**](https://www.openblas.net/) library, something like `/any_directory/libopenblas.so` should be returned.
 Therefore, there should be the name **openblas** in the **s**hared **o**bject returned (file extension **.so**).
+-->
 
-If the `ropenblas()` function can identify that the [**R**](https://www.r-project.org/) language is using the version of [**OpenBLAS**](https://www.openblas.net/) you wish to configure, a warning message will be returned asking if you really would like to proceed with the configuration again.
+<!-- If the `ropenblas()` function can identify that the [**R**](https://www.r-project.org/) language is using the version of [**OpenBLAS**](https://www.openblas.net/) you wish to configure, a warning message will be returned asking if you really would like to proceed with the configuration again.
+-->
 
-The `ropenblas()` function will download the desired version of the library [**OpenBLAS**](https://www.openblas.net/), compile and install the library in the `/opt` directory of your operational system.
+<!-- The `ropenblas()` function will download the desired version of the library [**OpenBLAS**](https://www.openblas.net/), compile and install the library in the `/opt` directory of your operational system.
 If the directory does not exist, it will be created so that the installation can be completed.
 Subsequently, files from the version of [**BLAS**](http://www.netlib.org/blas/) used in [**R**](https://www.r-project.org/) will be symbolically linked to the shared object files of the library version [**OpenBLAS**](https://www.openblas.net/) compiled and installed in `/opt`.
+-->
 
-You must be the operating system administrator to use this library.
+<!-- You must be the operating system administrator to use this library.
 Therefore, do not attempt to use it without telling your system administrator.
 If you have the ROOT password, you will be responsible for everything you do on your operating system.
+-->
 
-You will not necessarily have to run `ropenblas()` on every section of [**R**](https://www.r-project.org/).
+<!-- You will not necessarily have to run `ropenblas()` on every section of [**R**](https://www.r-project.org/).
 Almost always it will not be necessary.
@@
 Therefore, from time to time check using the command `extSoftVersion()["BLAS"]` if the link with [**OpenBLAS**](https://www.openblas.net/) is correct, otherwise run the command `ropenblas()` again.
+-->
 
@@
 
-```
-> last_version_r()
-$last_version
-[1] "4.0.3"
-
-$versions
-[1] "4.0.0" "4.0.1" "4.0.2" "4.0.3"
-
-$n
-[1] 4
+```{r, echo=FALSE}
+knitr::include_graphics(path = "inst/asciicast/last_version_r.svg")
 ```
 
-or
-
-```
-> last_version_r(major = 3L)
-$last_version
-[1] "3.6.3"
-
-$versions
- [1] "3.0.0"         "3.0.1"         "3.0.2"         "3.0.3"         "3.1.0"         "3.1.1"         "3.1.2"         "3.1.3"        
- [9] "3.2.0"         "3.2.1"         "3.2.2"         "3.2.3"         "3.2.4-revised" "3.2.4"         "3.2.5"         "3.3.0"        
-[17] "3.3.1"         "3.3.2"         "3.3.3"         "3.4.0"         "3.4.1"         "3.4.2"         "3.4.3"         "3.4.4"        
-[25] "3.5.0"         "3.5.1"         "3.5.2"         "3.5.3"         "3.6.0"         "3.6.1"         "3.6.2"         "3.6.3"
-
-$n
-[1] 32
-```
-
-**Note**: If `major = NULL`, the function will consider the major release number.
+<!-- **Note**: If `major = NULL`, the function will consider the major release number. -->
 
@@
 
-```
-> last_version_openblas()
-$last_version
-[1] "0.3.12"
-
-$versions
- [1] "0.1alpha1"   "0.1alpha2"   "0.1alpha2.1" "0.1alpha2.2" "0.1alpha2.3" "0.1alpha2.4" "0.1alpha2.5" "0.1.0"      
- [9] "0.1.1"       "0.2.0"       "0.2.1"       "0.2.2"       "0.2.3"       "0.2.4"       "0.2.5"       "0.2.6"      
-[17] "0.2.7"       "0.2.8"       "0.2.9"       "0.2.9.rc1"   "0.2.9.rc2"   "0.2.10"      "0.2.10.rc1"  "0.2.10.rc2" 
-[25] "0.2.11"      "0.2.12"      "0.2.13"      "0.2.14"      "0.2.15"      "0.2.16"      "0.2.16.rc1"  "0.2.17"     
-[33] "0.2.18"      "0.2.19"      "0.2.20"      "0.3.0"       "0.3.1"       "0.3.2"       "0.3.3"       "0.3.4"      
-[41] "0.3.5"       "0.3.6"       "0.3.7"       "0.3.8"       "0.3.9"       "0.3.10"      "0.3.11"      "0.3.12"
-
-$n
-[1] 48
+```{r, echo=FALSE}
+knitr::include_graphics(path = "inst/asciicast/last_version_openblas.svg")
 ```
@@
 
-```
-rcompiler()
+```{r, echo=FALSE}
+knitr::include_graphics(path = "inst/asciicast/rcompiler.svg")
 ```
@@
 
-In addition to the `x` argument, the` rcompiler()` function has two other arguments that will allow you to change and pass new compilation flags. Are they:
+<!-- In addition to the `x` argument, the` rcompiler()` function has two other arguments that will allow you to change and pass new compilation flags. Are they: -->
 
-1.
+<!-- 1.
 `with_blas`: This argument sets the `--with-blas` flag in the R language compilation process and must be passed as a string.
 Details on the use of this flag can be found [**here**](https://cran.r-project.org/doc/manuals/r-devel/R-admin.html).
-If `with_blas = NULL` (default), then it will be considered:
+If `with_blas = NULL` (default), then it will be considered: -->
 
-   ```
-   ./configure --prefix=/opt/R/version_r --enable-memory-profiling --enable-R-shlib --enable-threads=posix
-   --with-blas="-L/opt/OpenBLAS/lib -I/opt/OpenBLAS/include -lpthread -lm"
-   ```
+<!--    ``` -->
+<!--    ./configure --prefix=/opt/R/version_r --enable-memory-profiling --enable-R-shlib --enable-threads=posix -->
+<!--    --with-blas="-L/opt/OpenBLAS/lib -I/opt/OpenBLAS/include -lpthread -lm" -->
+<!--    ``` -->
 
-   Most likely, you will have little reason to change this argument.
+<!--    Most likely, you will have little reason to change this argument.
 Unless you know what you're doing, consider `with_blas = NULL`.
@@
 For a list of valid versions of [**R**](https://www.r-project.org/), run the `last_version_r()`.
-Installing [**R**](https://www.r-project.org/) in the `/opt/R/version_r` directory is important because some functions in the package require this.
+-->
+<!-- Installing [**R**](https://www.r-project.org/) in the `/opt/R/version_r` directory is important because some functions in the package require this.
 Both the [**R**](https://www.r-project.org/) language and the [**OpenBLAS**](https://www.openblas.net/) library will be installed in the `/opt` directory.
-If this directory does not exist in your GNU/Linux distribution, it will be created;
+If this directory does not exist in your GNU/Linux distribution, it will be created; -->
 
-2.
+<!-- 2.
 `complementary_flags`: String (`complementary_flags = NULL` by default) for adding complementary flags in the [**R**](https://www.r-project.org/) language compilation process.
-Passing a string to `complementary_flags` will compile it in the form:
+Passing a string to `complementary_flags` will compile it in the form: -->
 
-   ```
-    ./configure --with-blas="..." complementary_flags
-   ```
+<!--    ``` -->
+<!--     ./configure --with-blas="..." complementary_flags -->
+<!--    ``` -->
 
@@
 
-```
-link_again()
+```{r, echo=FALSE}
+knitr::include_graphics(path = "inst/asciicast/link_again.svg")
 ```

### 2020-12-15 inst/asciicast/example_asciicast_last_version_openblas.R

@@ -1,0 +1,7 @@
+#' Title: Using the last_version_openblas() function
+#' Rows: 24
+
+# The last_version_openblas() function automatically searches
+# OpenBLAS library versions in the official GitHub project.
+
+ropenblas::last_version_openblas()

### 2020-12-15 inst/asciicast/example_asciicast_last_version_r.R

@@ -1,0 +1,11 @@
+#' Title: Using the last_version_r() function
+
+ropenblas::last_version_r()
+
+# You can also specify the largest version
+
+ropenblas::last_version_r(major = 3L)
+
+# If major = NULL, the function will consider the major release number
+
+ropenblas::last_version_r(major = NULL)

### 2020-12-15 inst/asciicast/generating svg files.R

@@ -1,0 +1,23 @@
+cast <- asciicast::record("~/Downloads/ropenblas/inst/asciicast/example_asciicast_last_version_r.R")
+asciicast::write_svg(cast, path = "~/Downloads/ropenblas/inst/asciicast/last_version_r.svg",
+                     window = TRUE, cursor = TRUE)
+
+cast <- asciicast::record("~/Downloads/ropenblas/inst/asciicast/example_asciicast_last_version_openblas.R")
+asciicast::write_svg(cast, path = "~/Downloads/ropenblas/inst/asciicast/last_version_openblas.svg", window = TRUE,
+                     cursor = TRUE)
+
+cast <- asciicast::record("~/Downloads/ropenblas/inst/asciicast/example_asciicast_link_again.R")
+asciicast::write_svg(cast, path = "~/Downloads/ropenblas/inst/asciicast/link_again.svg", window = TRUE,
+                     cursor = TRUE)
+
+cast <- asciicast::record("~/Downloads/ropenblas/inst/asciicast/example_asciicast_ropenblas.R")
+asciicast::write_svg(cast, path = "~/Downloads/ropenblas/inst/asciicast/ropenblas.svg", window = TRUE,
+                     cursor = TRUE)
+
+cast <- asciicast::record("~/Downloads/ropenblas/inst/asciicast/example_asciicast_rcompiler.R")
+asciicast::write_svg(cast, path = "~/Downloads/ropenblas/inst/asciicast/rcompiler.svg", window = TRUE,
+                     cursor = TRUE)
+
+cast <- asciicast::record("~/Downloads/ropenblas/inst/asciicast/example_asciicast_install.R")
+asciicast::write_svg(cast, path = "~/Downloads/ropenblas/inst/asciicast/install.svg", window = TRUE,
+                     cursor = TRUE)

### 2020-12-16 inst/logo/creating_logo.R
Add new logo

@@ -1,0 +1,8 @@
+# remotes::install_github("GuangchuangYu/hexSticker")
+
+library(hexSticker)
+
+imgurl <- system.file("~/Downloads/ropenblas/inst/openblas_logo_01.png", package="hexSticker")
+
+sticker("~/Downloads/ropenblas/inst/molde.png", package="", p_size=22, s_x=1.03, s_y=.95, s_width=0.9,
+        filename="openblas_logo.png", h_fill="#000000", h_color="#929292", white_around_sticker = T)

### 2020-12-16 inst/logo/creating_logo.R
Add new logo

@@ -4,5 +4,5 @@ library(hexSticker)
 
 imgurl <- system.file("~/Downloads/ropenblas/inst/openblas_logo_01.png", package="hexSticker")
 
-sticker("~/Downloads/ropenblas/inst/molde.png", package="", p_size=22, s_x=1.03, s_y=.95, s_width=0.9,
+sticker("~/Downloads/ropenblas/inst/logo/molde.png", package="", p_size=22, s_x=1.03, s_y=.95, s_width=1,
         filename="openblas_logo.png", h_fill="#000000", h_color="#929292", white_around_sticker = T)

### 2020-12-16 CONTRIBUTING.Rmd
Update logo and website

---
title: Contributing to the development of the ropenbals package
author: |
  | **Package website**: **<https://prdm0.github.io/ropenblas>**
  |
  | **Summary**
output: 
  bookdown::github_document2:
    number_sections: true
    toc: true
    toc_depth: 2
toccolor: 'blue'
---

# General information

The **ropenblas** package introduces a simple way, through its functions, to link the library [**OpenBLAS**](https://www.openblas.net/) with the language [**R**](https: //www.r-project.org/). In addition, with ropenblas it is possible to link different versions of R, making it possible to easily switch between the different versions of R compiled.

The package currently works only on GNU/Linux systems and is independent of the official repositories of the user's GNU/Linux distribution. This allows the R user on GNU/Linux systems who is the administrator of the operating system - OS to link the latest versions of R and OpenBLAS as well as switch between versions if they wish.

# Main contributions

The main contributions to the **ropenblas** package are listed below:

  1. Revision of the code to detect possible inconsistent points that may cause the functions provided by the package to fail in some GNU / Linux distribution;
  2. Test the package on different GNU / Linux distributions, reporting possible inconsistencies at <https://github.com/prdm0/ropenblas/issues>;
  3. Improved English for package messages and documentation;
  4. Improved writing of job documentation;
  5. Allow Windows system users to take advantage of the `ropenblas()` function. One suggestion would be to link precompiled binaries from the OpenBLAS library and distribute them in a `inst/` directory.

### 2020-12-16 README.Rmd
Updating directories, packages and minor changes

@@
 
+**ropenblas** <a href='logo.png'><img src='logo.png' align="right" height="139" /></a>
+
 [![last](https://www.r-pkg.org/badges/last-release/ropenblas)](https://CRAN.R-project.org/package=ropenblas)
@@
 
-<img src="https://raw.githubusercontent.com/prdm0/ropenblas/master/logo.png" height="270" width="250" align="right" />
+</br>
+</br>
+<!-- <img src="https://raw.githubusercontent.com/prdm0/ropenblas/master/logo.png" height="270" width="250" align="right" /> -->
 
@@
 ```{r, fig.align='center',  echo=FALSE}
-knitr::include_graphics(path = "inst/asciicast/ropenblas.svg")
+knitr::include_graphics(path = "img/asciicast/ropenblas.svg")
 ```
@@
 ```{r, echo=FALSE}
-knitr::include_graphics(path = "inst/asciicast/last_version_r.svg")
+knitr::include_graphics(path = "img/asciicast/last_version_r.svg")
 ```
@@
 ```{r, echo=FALSE}
-knitr::include_graphics(path = "inst/asciicast/last_version_openblas.svg")
+knitr::include_graphics(path = "img/asciicast/last_version_openblas.svg")
 ```
@@
 ```{r, echo=FALSE}
-knitr::include_graphics(path = "inst/asciicast/rcompiler.svg")
+knitr::include_graphics(path = "img/asciicast/rcompiler.svg")
 ```
@@
 ```{r, echo=FALSE}
-knitr::include_graphics(path = "inst/asciicast/link_again.svg")
+knitr::include_graphics(path = "img/asciicast/link_again.svg")
 ```

### 2020-12-16 README.Rmd
Update site.
Update website.
Update website
Update size logo

--- 2020-12-15 README.Rmd
@@
 
+**ropenblas** 
+<a href='logo.png'><img src='logo.png' align="right" height="175" /></a>
+
 [![last](https://www.r-pkg.org/badges/last-release/ropenblas)](https://CRAN.R-project.org/package=ropenblas)
@@
 
-<img src="https://raw.githubusercontent.com/prdm0/ropenblas/master/logo.png" height="270" width="250" align="right" />
+<br/><br/><br/>
+
+<!-- <img src="https://raw.githubusercontent.com/prdm0/ropenblas/master/logo.png" height="270" width="250" align="right" /> -->
 
@@
 ```{r, fig.align='center',  echo=FALSE}
-knitr::include_graphics(path = "inst/asciicast/ropenblas.svg")
+knitr::include_graphics(path = "https://raw.githubusercontent.com/prdm0/ropenblas/bce920c05f8daa13fc6568e6797d4b841e9d43ce/img/asciicast/ropenblas.svg")
 ```
@@
 ```{r, echo=FALSE}
-knitr::include_graphics(path = "inst/asciicast/last_version_r.svg")
+knitr::include_graphics(path = "https://raw.githubusercontent.com/prdm0/ropenblas/bce920c05f8daa13fc6568e6797d4b841e9d43ce/img/asciicast/last_version_r.svg")
 ```
@@
 ```{r, echo=FALSE}
-knitr::include_graphics(path = "inst/asciicast/last_version_openblas.svg")
+knitr::include_graphics(path = "https://raw.githubusercontent.com/prdm0/ropenblas/bce920c05f8daa13fc6568e6797d4b841e9d43ce/img/asciicast/last_version_openblas.svg")
 ```
@@
 ```{r, echo=FALSE}
-knitr::include_graphics(path = "inst/asciicast/rcompiler.svg")
+knitr::include_graphics(path = "https://raw.githubusercontent.com/prdm0/ropenblas/bce920c05f8daa13fc6568e6797d4b841e9d43ce/img/asciicast/rcompiler.svg")
 ```
@@
 ```{r, echo=FALSE}
-knitr::include_graphics(path = "inst/asciicast/link_again.svg")
+knitr::include_graphics(path = "https://raw.githubusercontent.com/prdm0/ropenblas/bce920c05f8daa13fc6568e6797d4b841e9d43ce/img/asciicast/link_again.svg")
 ```

### 2020-12-17 paper/paper.Rmd
update

@@
 
-The functions of the `ropenblas` package can help the R language user to make this link without leaving the R promprt, as well as allowing the user to choose the version of OpenBLAS to be considered, the last stable version being considered by default .
+<!-- The functions of the `ropenblas` package can help the R language user to make this link without leaving the R promprt, as well as allowing the user to choose the version of OpenBLAS to be considered, the last stable version being considered by default .
 Everything is accomplished by functions without many arguments and without major complications to be used.
 These functions can be very comforting for users of R on GNU/Linux systems who do not feel safe to run several codes in a terminal that runs Shell Script codes for the language configuration.
+-->
 
-It is very common to see users of R in distributions with repositories not prone to immediate updates of programs using several tutorials found in communities on the internet suggesting several lines of code and steps that can be potentially dangerous or easy to be misunderstood by many users of R language.
+<!-- It is very common to see users of R in distributions with repositories not prone to immediate updates of programs using several tutorials found in communities on the internet suggesting several lines of code and steps that can be potentially dangerous or easy to be misunderstood by many users of R language.
 Being able to compile, enable resources if necessary and switch between versions of R using simple functions to be used and without leaving the command pompt of the R language is attractive.
+-->
 
-# General package information
+<!-- # General package information -->
 
@@
 Everything will be done automatically regardless of the Linux distribution you are using.
+Enumerating some advantages of the package:
 
-The `ropenblas` package is already available on the Comprehensive R Archive Network - CRAN, currently in version 0.2.8 and the project is maintained on GitHub at  <https://github.com/prdm0/ropenblas> where contributors can find others details of the code, information, as well as being able to contribute with the development of the project.
+<!-- The `ropenblas` package is already available on the Comprehensive R Archive Network - CRAN, currently in version 0.2.8 and the project is maintained on GitHub at  <https://github.com/prdm0/ropenblas> where contributors can find others details of the code, information, as well as being able to contribute with the development of the project.
 Information can also be found on the project website.
@@
 Suggestions for improvements and bug reports can be sent via the link <https://github.com/prdm0/ropenblas/issues>.
+-->
 
@@
 
-You can also specify older versions of the OpenBLAS library. Automatically, if no version is specified, the `ropenblas` package will consider the latest version of the library OpenBLAS.
+<!-- You can also specify older versions of the OpenBLAS library. Automatically, if no version is specified, the `ropenblas` package will consider the latest version of the library OpenBLAS.  -->
 
-Considering using the OpenBLAS library rather than the BLAS may bring extra optimizations for your code and improved computational performance for your simulations, since OpenBLAS is an optimized implementation of the library BLAS.
+<!-- Considering using the OpenBLAS library rather than the BLAS may bring extra optimizations for your code and improved computational performance for your simulations, since OpenBLAS is an optimized implementation of the library BLAS.
+-->
 
-Some of the reasons why it is convenient to link R language to the use of BLAS optimized alternatives can be found here.
+<!-- Some of the reasons why it is convenient to link R language to the use of BLAS optimized alternatives can be found here.
 Several other benchmarks that point to improved computing performance by considering the library OpenBLAS can be found on the internet.
+-->
 
-The `ropenblas` package, by `rcompiler()` function is also useful if you want to install different versions of the R language.
+<!-- The `ropenblas` package, by `rcompiler()` function is also useful if you want to install different versions of the R language.
 The different versions, specified by the user of the R language, will be compiled and will also be linked to the OpenBLAS library.
@@
 Another great use of the `rcompiler()` function is that you will not be dependent on updating your GNU/Linux distribution repositories and you can always have the latest version of the R language.
+-->
 
-The use of the `ropenblas` package will return warnings that help you proceed with the use of the functions.
+<!-- The use of the `ropenblas` package will return warnings that help you proceed with the use of the functions.
 If your internet is not working or if any dependency on the operating system is not present, the package will let you know.
-Enumerating some advantages of the package:
+-->
 
@@
 
-# Dependencies
+<!-- # Dependencies -->
 
-In addition to dependencies in the form of other packages deposited with CRAN, the `ropenblas` package depends on external dependencies that are normally installed or are easily installed on any GNU/Linux distribution.
-Are they:
+<!-- In addition to dependencies in the form of other packages deposited with CRAN, the `ropenblas` package depends on external dependencies that are normally installed or are easily installed on any GNU/Linux distribution.
+Are they: -->
 
-  1. **GNU Make**: GNU Make utility to maintain groups of programs; 
-  2. **GNU GCC Compiler (C and Fortran)**: The GNU Compiler Collection - C and Fortran frontends.
+<!--   1. **GNU Make**: GNU Make utility to maintain groups of programs;  -->
+<!--   2. **GNU GCC Compiler (C and Fortran)**: The GNU Compiler Collection - C and Fortran frontends. -->
 
@@
 
-# Installation
+# Brief explanation
+
+<!-- # Installation -->
 
@@
 The first is using the `install.packages()` function of the `utils` package which is available in any basic language installation and the second is using the `devtools` package which will allow the package to be installed directly from the development directory on GitHub.
-All code kept in the master branch of the package project on GitHub can be installed, since there will only be codes that are working properly and ready to use.
-The two forms of installation follow:
 
-  1. `install.packages("ropenblas")`: for installing the package available at CRAN;
-  2. `devtools::install_github(repo = "prdm0/ropenblas, ref = "master", force = TRUE)`: for installing the package from the project development directory on GitHub.
+<!-- All code kept in the master branch of the package project on GitHub can be installed, since there will only be codes that are working properly and ready to use.
+The two forms of installation follow: -->
 
-# Exported functions and usage
+<!--   1. `install.packages("ropenblas")`: for installing the package available at CRAN; -->
+<!--   2. `devtools::install_github(repo = "prdm0/ropenblas, ref = "master", force = TRUE)`: for installing the package from the project development directory on GitHub. -->
+
+<!-- # Exported functions and usage -->
 
@@
 
-The following subsections are intended to explain and exemplify the use of these functions focused on the main problems that can be solved using the `ropenblas` package.
+<!-- The following subsections are intended to explain and exemplify the use of these functions focused on the main problems that can be solved using the `ropenblas` package.
 Some functions may take a few minutes to run, as they are responsible for compiling code that is considerably larges and complicateds.
 This is the case with the `rcompiler()` and  `ropenblas()` functions.
+-->
 
@@
 Therefore, for the argument `major` a number must be passed, preferably an integer that indicates which is the largest version to be considered.
-Consider the example:
 
-```{r packages, echo=FALSE, cache=TRUE}
-library("ropenblas")
-```
+<!-- Consider the example: -->
 
-```{r, prompt=TRUE, dependson="ropenblas", cache=TRUE}
-last_version_r(major = 4L)
-```
+<!-- ```{r packages, echo=FALSE, cache=TRUE} -->
+<!-- library("ropenblas") -->
+<!-- ``` -->
+
+<!-- ```{r, prompt=TRUE, dependson="ropenblas", cache=TRUE, eval=FALSE} -->
+<!-- last_version_r(major = 4L) -->
+<!-- ``` -->
 
@@
 
-The function is always adapted to search for new versions and will understand the new language updates since it has been implemented in a general way.
+<!-- The function is always adapted to search for new versions and will understand the new language updates since it has been implemented in a general way.
 Therefore, `last_version_r(major = NULL)$last_version` will always return the latest version of R and not the latest version of R available in the repositories of your GNU/Linux distribution.
 Therefore, it may be that, depending on when this function is performed, different results may occur.
+-->
 
@@
 The `last_version_openblas()` function works similarly to the `last_version_r()` function, returning a list of three elements named in the same way with the information from the latest version, all the versions and the number of versions of the OpenBLAS library, respectively.
-Unlike the `last_version_r()` function that searches for the versions of R on the official language website, the `last_version_openblas()` function will search for information on the OpenBLAS library versions on official language development repository on GitHub.
+
+<!-- Unlike the `last_version_r()` function that searches for the versions of R on the official language website, the `last_version_openblas()` function will search for information on the OpenBLAS library versions on official language development repository on GitHub.
 In addition, due to the way that the versions of the OpenBLAS library are numbered, the function will always consider the universe of all versions of the OpenBLAS library, therefore, being a function without arguments.
@@
 Just like the `last_version_r()` function, the `last_version_openblas()` function does not depend on which version of OpenBLAS is available in the repositories of your GNU/Linux distribution.
+-->
 
@@
 
-```{r, echo=FALSE, message=FALSE, warning=FALSE, fig.align='center', fig.cap="Window for entering the system administration password.", out.width="55%"}
-knitr::include_graphics("root.png")
-```
+<!-- ```{r, echo=FALSE, message=FALSE, warning=FALSE, fig.align='center', fig.cap="Window for entering the system administration password.", out.width="55%"} -->
+<!-- knitr::include_graphics("root.png") -->
+<!-- ``` -->
 
-If the user is running the R language in a terminal of the GNU/Linux distribution, a Shell Bash type terminal, they will be asked to include the password by the terminal itself.
+<!-- If the user is running the R language in a terminal of the GNU/Linux distribution, a Shell Bash type terminal, they will be asked to include the password by the terminal itself.
 The function will not change the operation of other programs, nor even major changes will be made in the initial version of R, just summarizing the creation of symbolic links.
+-->
 
-The general way of using the function is given by:
+<!-- The general way of using the function is given by: -->
 
-**General use**:
+<!-- **General use**: -->
 
@@
 
-The function's arguments are described below:
+<!-- The function's arguments are described below: -->
 
@@
 
-If the goal is to install the R language, switch between versions of R, and link the installed versions of the language with the OpenBLAS library, you shouldn't have to worry about the `with_blas` and `complementary_flags` arguments, respectively.
+<!-- If the goal is to install the R language, switch between versions of R, and link the installed versions of the language with the OpenBLAS library, you shouldn't have to worry about the `with_blas` and `complementary_flags` arguments, respectively.
 These arguments are useful for a minority of programmers who feel very specific needs to pass complementary flags to be considered in the R language compilation process, inclusion of complementary library directories, among other arguments that can be found in the official language manuals.
-By default, if nothing is passed to the `with_blas` and `complementary_flags` arguments, the compilation will be performed as follows:
+By default, if nothing is passed to the `with_blas` and `complementary_flags` arguments, the compilation will be performed as follows: -->
 
-```{bash, eval=FALSE}
-./configure --prefix=/opt/R/version_r --enable-memory-profiling 
---enable-R-shlib --enable-threads=posix 
---with-blas="-L/opt/OpenBLAS/lib -I/opt/OpenBLAS/include
--lpthread -lm"
-```
+<!-- ```{bash, eval=FALSE} -->
+<!-- ./configure --prefix=/opt/R/version_r --enable-memory-profiling  -->
+<!-- --enable-R-shlib --enable-threads=posix  -->
+<!-- --with-blas="-L/opt/OpenBLAS/lib -I/opt/OpenBLAS/include -->
+<!-- -lpthread -lm" -->
+<!-- ``` -->
 
-As a suggestion and if you want to use the complementary arguments, that is, use `with_blas` and `complementary_flags`, do not change the directory `include` and `lib` of the OpenBLAS library in argument `with_blas`, considering that the `rcompiler()` function will always install the OpenBLAS library in the `/opt/OpenBLAS` directory, thus avoiding problems with breaking important links on your system and in the configuration of the initial version of R.
+<!-- As a suggestion and if you want to use the complementary arguments, that is, use `with_blas` and `complementary_flags`, do not change the directory `include` and `lib` of the OpenBLAS library in argument `with_blas`, considering that the `rcompiler()` function will always install the OpenBLAS library in the `/opt/OpenBLAS` directory, thus avoiding problems with breaking important links on your system and in the configuration of the initial version of R.
 If you try to pass a different installation directory to the OpenBLAS library, the `rcompiler()` function will disregard this installation of OpenBLAS and perform a safe installation in the `/opt/OpenBLAS` directory.
@@
 This allows no errors to be made and unforeseen bugs to occur.
-If there are reasons to consider complementary strings for the arguments `with_blas` and `complementary_flags`, the R language will be compiled as follows:
+If there are reasons to consider complementary strings for the arguments `with_blas` and `complementary_flags`, the R language will be compiled as follows: -->
 
-```{bash, eval=FALSE}
---prefix=/opt/R/version_r --enable-memory-profiling --enable-R-shlib
---enable-threads=posix --with-blas="..." complementary_flags
-```
+<!-- ```{bash, eval=FALSE} -->
+<!-- --prefix=/opt/R/version_r --enable-memory-profiling --enable-R-shlib -->
+<!-- --enable-threads=posix --with-blas="..." complementary_flags -->
+<!-- ``` -->
 
-The `rcompiler()` function will also avoid unnecessary compilations.
+<!-- The `rcompiler()` function will also avoid unnecessary compilations.
 Therefore, if your initial version of R is already linked to some version of the OpenBLAS library, only the R language will be compiled, with no need to compile the OpenBLAS library.
@@
 Below I will exemplify some situations in which the use of the `rcompiler()` function may be convenient.
+-->
 
-**Example**: In the hypothetical situation of an R user on any GNU/Linux distribution, if are interested in knowing the latest version of the R language, installing it and linking it to the OpenBLAS library, it should proceed as follows:
+<!-- **Example**: In the hypothetical situation of an R user on any GNU/Linux distribution, if are interested in knowing the latest version of the R language, installing it and linking it to the OpenBLAS library, it should proceed as follows: -->
 
-```{r, eval=FALSE, prompt=TRUE}
-rcompiler(x = "4.0.2") # or simply rcompiler () or rcompiler (x = NULL)
-```
+<!-- ```{r, eval=FALSE, prompt=TRUE} -->
+<!-- rcompiler(x = "4.0.2") # or simply rcompiler () or rcompiler (x = NULL) -->
+<!-- ``` -->
 
-After executing the function, everything will be ready, and can be checked by executing the command `extSoftVersion()["BLAS"]` in the next execution of R, that is, in a new instance.
+<!-- After executing the function, everything will be ready, and can be checked by executing the command `extSoftVersion()["BLAS"]` in the next execution of R, that is, in a new instance.
 Thus the user will know that the compilation of the R library, and if necessary, of the OpenBLAS library was carried out as requested.
-Briefly, the `extSoftVersion()["BLAS"]` command will return something like:
+Briefly, the `extSoftVersion()["BLAS"]` command will return something like: -->
 
-```{r, prompt=TRUE}
-extSoftVersion()["BLAS"]
-```
+<!-- ```{r, prompt=TRUE} -->
+<!-- extSoftVersion()["BLAS"] -->
+<!-- ``` -->
 
@@
 
-**Example**: In a new hypothetical situation of a user of R having installed two different versions of the R language as presented above, using the function `rcompiler()`, for example, versions 3.6.3 and 4.0.0, so:
+<!-- **Example**: In a new hypothetical situation of a user of R having installed two different versions of the R language as presented above, using the function `rcompiler()`, for example, versions 3.6.3 and 4.0.0, so: -->
 
-```{r, eval=FALSE, prompt=TRUE}
-# First installation of R performed by the rcompiler() function:
-rcompiler(x = "4.0.0") 
-# Second installation of R performed by the rcompiler() function:
-rcompiler(x = "3.6.3")
-# Returning version 4.0.0 from R:
-rcompiler(x = "4.0.0")
-```
+<!-- ```{r, eval=FALSE, prompt=TRUE} -->
+<!-- # First installation of R performed by the rcompiler() function: -->
+<!-- rcompiler(x = "4.0.0")  -->
+<!-- # Second installation of R performed by the rcompiler() function: -->
+<!-- rcompiler(x = "3.6.3") -->
+<!-- # Returning version 4.0.0 from R: -->
+<!-- rcompiler(x = "4.0.0") -->
+<!-- ``` -->
 
-Running the code `rcompiler(x = "4.0.0")` as the last line of the example above will allow the user to link the binaries previously created in the 4.0.0 compilation process when `rcompiler(x = "4.0.0")` was run for the first time.
+<!-- Running the code `rcompiler(x = "4.0.0")` as the last line of the example above will allow the user to link the binaries previously created in the 4.0.0 compilation process when `rcompiler(x = "4.0.0")` was run for the first time.
 This will avoid a compilation so that switching between versions of R that have already been compiled will be quick and easy.
 Although this seems ideal and it is, the function will ask if the user wants to recompile an already compiled version.
+-->
 
@@
 
-Unlike the `rcompiler()` function that will allow multiple versions of R to be available in your GNU/Linux distribution, the `ropenblas()` function will allow only one version of the OpenBLAS library to be installed.
+<!-- Unlike the `rcompiler()` function that will allow multiple versions of R to be available in your GNU/Linux distribution, the `ropenblas()` function will allow only one version of the OpenBLAS library to be installed.
 The function will allow versions of OpenBLAS $\geq 0.3.0$ to be installed.
 Even if the function `rcompile()` responsible for compiling and installing the R language has not been used, the function `ropenblas()` may link a version of OpenBLAS to the main installation of R, that is, even if the R is installed by procedures external to the package.
+-->
 
-**General use**:
+<!-- **General use**: -->
 
@@
 
-  - `x`: String with the version of the OpenBLAS library to be compiled, installed and linked with the main R installation;
+  - `x`: String with the version of the OpenBLAS library to be compiled, installed and linked with the main R installation (by default it is considered the latest version);
   - `restart_r`: Logical value (default `restart_r = TRUE`) to update the R section after compiling, installing and linking the OpenBLAS library.
-\end{itemize}
 
-By default, if `x = NULL` the latest version of the OpenBLAS library will be considered.
+<!-- By default, if `x = NULL` the latest version of the OpenBLAS library will be considered.
 This is equivalent to passing `last_version_openblas()$last_version` to `x`.
-There are no great reasons to consider an older version of the OpenBLAS library, although the `ropenblas` package will allow this to be done in a simple way, as in the following example:
+There are no great reasons to consider an older version of the OpenBLAS library, although the `ropenblas` package will allow this to be done in a simple way, as in the following example:  -->
 
-**Example**: Regardless of how the R language was installed, suppose you want to compile, install and link the latest version of the OpenBLAS library to the R language. This can be done by doing:
+<!-- **Example**: Regardless of how the R language was installed, suppose you want to compile, install and link the latest version of the OpenBLAS library to the R language.
+This can be done by doing: -->
 
-```{r, eval=FALSE, prompt=TRUE}
-ropenblas()
-```
+<!-- ```{r, eval=FALSE, prompt=TRUE} -->
+<!-- ropenblas() -->
+<!-- ``` -->
 
-```{r, echo=FALSE, message=FALSE, warning=FALSE, fig.align='center', fig.cap="Output informing the end of the procedure for linking the OpenBLAS library to the R language.", out.width="100%"}
-knitr::include_graphics("ropenblas_01.png")
-```
+<!-- ```{r, echo=FALSE, message=FALSE, warning=FALSE, fig.align='center', fig.cap="Output informing the end of the procedure for linking the OpenBLAS library to the R language.", out.width="100%"} -->
+<!-- knitr::include_graphics("ropenblas_01.png") -->
+<!-- ``` -->
 
-**Example**: In situations where the latest version of the OpenBLAS library is already installed, if the user wishes to install a previous version of OpenBLAS, for example the version $0.3.8$, he should make it clear by answering a question, as shown in the image below:
+<!-- **Example**: In situations where the latest version of the OpenBLAS library is already installed, if the user wishes to install a previous version of OpenBLAS, for example the version $0.3.8$, he should make it clear by answering a question, as shown in the image below: -->
 
-```{r, eval=FALSE, prompt=TRUE}
-ropenblas("0.3.8")
-```
+<!-- ```{r, eval=FALSE, prompt=TRUE} -->
+<!-- ropenblas("0.3.8") -->
+<!-- ``` -->
 
-```{r, echo=FALSE, message=FALSE, warning=FALSE, fig.align='center', fig.cap="Asking if the user really wants to compile and link an older version of the OpenBLAS library.", out.width="100%"}
-knitr::include_graphics("ropenblas_02.png")
-```
+<!-- ```{r, echo=FALSE, message=FALSE, warning=FALSE, fig.align='center', fig.cap="Asking if the user really wants to compile and link an older version of the OpenBLAS library.", out.width="100%"} -->
+<!-- knitr::include_graphics("ropenblas_02.png") -->
+<!-- ``` -->
 
@@
 The function be able to link again the R language with the OpenBLAS library.
-Thus, `link_again()` will only make the relinkagem when in some previous section of R the `ropenblas()` function has been used for the initial binding of the R language with the OpenBLAS library.
 
-The use of the function is quite simple, just by running the code `link_again()`, since the function has no arguments.
+<!-- Thus, `link_again()` will only make the relinkagem when in some previous section of R the `ropenblas()` function has been used for the initial binding of the R language with the OpenBLAS library.
+-->
+
+<!-- The use of the function is quite simple, just by running the code `link_again()`, since the function has no arguments.
 It will automatically detect if there was a link break that will be rebuilt again without the need for any compilation.
@@
 Link breakage rarely occurs, but if it does, it can be resolved quickly.
-The following code and image exemplify a possible reconstruction of symbolic links using the `link_again()` function:
+The following code and image exemplify a possible reconstruction of symbolic links using the `link_again()` function: -->
 
@@
 
-```{r, echo=FALSE, message=FALSE, warning=FALSE, fig.align='center', fig.cap="If an unlinking of the OpenBLAS library occurs, the function will re-link the library.", out.width="100%"}
-knitr::include_graphics("link_again_01.png")
-```
+<!-- ```{r, echo=FALSE, message=FALSE, warning=FALSE, fig.align='center', fig.cap="If an unlinking of the OpenBLAS library occurs, the function will re-link the library.", out.width="100%"} -->
+<!-- knitr::include_graphics("link_again_01.png") -->
+<!-- ``` -->
 
@@
 
-Returns the contents of the `NEWS.html` file in the standard browser installed on the operating system.
+The `rnews()` function returns the contents of the `NEWS.html` file in the standard browser installed on the operating system.
 The `NEWS.html` file contains the main changes from the recently released versions of the R language.
 The goal is to facilitate the query by invoking it directly from the R command prompt.
-The `rnews()` function is analogous to the news function of the `utils` package.
-However, using the news command in a terminal style bash shell is possible to receive a message like:
 
-```{r, eval=FALSE}
-news()
-## starting httpd help server ... done
-## Error in browseURL(url): 'browser' must be a non-empty character string
-```
+<!-- The `rnews()` function is analogous to the news function of the `utils` package. However, using the news command in a terminal style bash shell is possible to receive a message like: -->
 
-If `pdf = FALSE` (default), the `NEWS.html` file will open in the browser, otherwise `NEWS.pdf` will be opened.
+<!-- ```{r, eval=FALSE} -->
+<!-- news() -->
+<!-- ## starting httpd help server ... done -->
+<!-- ## Error in browseURL(url): 'browser' must be a non-empty character string -->
+<!-- ``` -->
+
+<!-- If `pdf = FALSE` (default), the `NEWS.html` file will open in the browser, otherwise `NEWS.pdf` will be opened.
 If `dev = FALSE` (default), it will not show changes made to the language development version.
 To see changes in the development version, do `dev = TRUE`.
+-->
 

### 2021-03-08 README.Rmd
Update website + size logo
Update paper

@@
 author: |
-  | **Package website**: **<https://prdm0.github.io/ropenblas>**
   |
@@
   | **Summary**
+  | **Package website**: **<https://prdm0.github.io/ropenblas>**
 output: 
@@
 toccolor: 'blue'
+editor_options: 
+  markdown: 
+    wrap: 72
 ---
@@
 **ropenblas**
-<a href='logo.png'><img src='logo.png' align="right" height="175" /></a>
 
@@
 
-<br/><br/><br/>
+```{r, fig.align='center', echo=FALSE, out.width=219}
+knitr::include_graphics("https://raw.githubusercontent.com/prdm0/ropenblas/master/logo.png")
+```
 
@@
 
-The [**ropenblas**](https://prdm0.github.io/ropenblas/) is a package designed to facilitate the linking of the library [**OpenBLAS**](https://www.openblas.net/) with the language [**R**](https://www.r-project.org/).
-The package, which works only for Linux systems, will automatically download the latest source code from the [**OpenBLAS**](https://www.openblas.net/) library and compile the code.
-The package will automatically bind the language [**R**](https://www.r-project.org/), through the `ropenblas()` function, to use the [**OpenBLAS**](https://www.openblas.net/) library.
-Everything will be done automatically regardless of the Linux distribution you are using.
+The [**ropenblas**](https://prdm0.github.io/ropenblas/) is a package
+designed to facilitate the linking of the library
+[**OpenBLAS**](https://www.openblas.net/) with the language
+[**R**](https://www.r-project.org/). The package, which works only for
+Linux systems, will automatically download the latest source code from
+the [**OpenBLAS**](https://www.openblas.net/) library and compile the
+code. The package will automatically bind the language
+[**R**](https://www.r-project.org/), through the `ropenblas()` function,
+to use the [**OpenBLAS**](https://www.openblas.net/) library. Everything
+will be done automatically regardless of the Linux distribution you are
+using.
 
-You can also specify older versions of the [**OpenBLAS**](https://www.openblas.net/) library.
-Automatically, if no version is specified, the [**ropenblas**](https://prdm0.github.io/ropenblas/) package will consider the latest version of the library [**OpenBLAS**](https://www.openblas.net/).
+You can also specify older versions of the
+[**OpenBLAS**](https://www.openblas.net/) library. Automatically, if no
+version is specified, the
+[**ropenblas**](https://prdm0.github.io/ropenblas/) package will
+consider the latest version of the library
+[**OpenBLAS**](https://www.openblas.net/).
 
-Considering using the [**OpenBLAS**](https://www.openblas.net/) library rather than the [**BLAS**](http://www.netlib.org/blas/) may bring extra optimizations for your code and improved computational performance for your simulations, since [**OpenBLAS**](https://www.openblas.net/) is an optimized implementation of the library [**BLAS**](http://www.netlib.org/blas/).
+Considering using the [**OpenBLAS**](https://www.openblas.net/) library
+rather than the [**BLAS**](http://www.netlib.org/blas/) may bring extra
+optimizations for your code and improved computational performance for
+your simulations, since [**OpenBLAS**](https://www.openblas.net/) is an
+optimized implementation of the library
+[**BLAS**](http://www.netlib.org/blas/).
 
-Some of the reasons why it is convenient to link [**R**](https://www.r-project.org/) language to the use of [**BLAS**](http://www.netlib.org/blas/) optimized alternatives can be found [**here**](https://csantill.github.io/RPerformanceWBLAS/).
-Several other [**benchmarks**](https://en.wikipedia.org/wiki/Benchmarking) that point to improved computing performance by considering the library [**OpenBLAS**](https://www.openblas.net/) can be found on the internet.
+Some of the reasons why it is convenient to link
+[**R**](https://www.r-project.org/) language to the use of
+[**BLAS**](http://www.netlib.org/blas/) optimized alternatives can be
+found [**here**](https://csantill.github.io/RPerformanceWBLAS/). Several
+other [**benchmarks**](https://en.wikipedia.org/wiki/Benchmarking) that
+point to improved computing performance by considering the library
+[**OpenBLAS**](https://www.openblas.net/) can be found on the internet.
 
-The ropenblas package, by `rcompiler()` function is also useful if you want to install different versions of the [**R**](https://www.r-project.org/) language.
-The different versions, specified by the user of the [**R**](https://www.r-project.org/) language, will be compiled and will also be linked to the [**OpenBLAS**](https://www.openblas.net/) library.
-If you want to switch between compiled versions of the [**R**](https://www.r-project.org/) language, no compilation is needed anymore.
-This allows you to avoid having to get your hands dirty with tedious operating system settings, regardless of your GNU/Linux distribution.
-Another great use of the `rcompiler()` function is that you will not be dependent on updating your GNU/Linux distribution repositories and you can always have the latest version of the [**R**](https://www.r-project.org/) language.
+The ropenblas package, by `rcompiler()` function is also useful if you
+want to install different versions of the
+[**R**](https://www.r-project.org/) language. The different versions,
+specified by the user of the [**R**](https://www.r-project.org/)
+language, will be compiled and will also be linked to the
+[**OpenBLAS**](https://www.openblas.net/) library. If you want to switch
+between compiled versions of the [**R**](https://www.r-project.org/)
+language, no compilation is needed anymore. This allows you to avoid
+having to get your hands dirty with tedious operating system settings,
+regardless of your GNU/Linux distribution. Another great use of the
+`rcompiler()` function is that you will not be dependent on updating
+your GNU/Linux distribution repositories and you can always have the
+latest version of the [**R**](https://www.r-project.org/) language.
 
-The use of the ropenblas package will return warnings that help you proceed with the use of the functions.
-If your internet is not working or if any dependency on the operating system is not present, the package will let you know.
+The use of the ropenblas package will return warnings that help you
+proceed with the use of the functions. If your internet is not working
+or if any dependency on the operating system is not present, the package
+will let you know.
 
@@
 
-Some advantages of using the [**ropenblas**](https://prdm0.github.io/ropenblas/) library:
+Some advantages of using the
+[**ropenblas**](https://prdm0.github.io/ropenblas/) library:
 
-   - Everything is done within the [**R**](https://www.r-project.org/) language;
+-   Everything is done within the [**R**](https://www.r-project.org/)
+    language;
 
@@
 
-   - The [**OpenBLAS**](https://www.openblas.net/) library will be compiled and you will choose which build version to bind to [**R**](https://www.r-project.org/), regardless of your Linux distribution;
+-   The [**OpenBLAS**](https://www.openblas.net/) library will be
+    compiled and you will choose which build version to bind to
+    [**R**](https://www.r-project.org/), regardless of your Linux
+    distribution;
 
-   - If your GNU/Linux distribution does not have updated versions of [**OpenBLAS**](https://www.openblas.net/), it matters little.
-The ropenblas package fetches the latest stable release of the [**OpenBLAS**](https://www.openblas.net/) library development account on GitHub;
+-   If your GNU/Linux distribution does not have updated versions of
+    [**OpenBLAS**](https://www.openblas.net/), it matters little. The
+    ropenblas package fetches the latest stable release of the
+    [**OpenBLAS**](https://www.openblas.net/) library development
+    account on GitHub;
 
-   - You do not need to know Linux well.
-In some distributions, it may not be so simple for a less experienced user to compile and link the library to the [**OpenBLAS**](https://www.openblas.net/) library with the [**R**](https://www.r-project.org/) language;
+-   You do not need to know Linux well. In some distributions, it may
+    not be so simple for a less experienced user to compile and link the
+    library to the [**OpenBLAS**](https://www.openblas.net/) library
+    with the [**R**](https://www.r-project.org/) language;
 
-   - It is much easier to direct a person to link [**OpenBLAS**](https://www.openblas.net/) with [**R**](https://www.r-project.org/) saying "run `ropenblas()` within [**R**](https://www.r-project.org/)" than asking that person to verify that an unoptimized version of [**BLAS**](http://www.netlib.org/blas/) installed on the system.
-Then you have to guide the removal of the unoptimized version of [**BLAS**](http://www.netlib.org/blas/) and guide it to the installation of the library [**OpenBLAS**](https://www.openblas.net/) through the most diverse procedures depending on the GNU/Linux distribution used;
+-   It is much easier to direct a person to link
+    [**OpenBLAS**](https://www.openblas.net/) with
+    [**R**](https://www.r-project.org/) saying "run `ropenblas()` within
+    [**R**](https://www.r-project.org/)" than asking that person to
+    verify that an unoptimized version of
+    [**BLAS**](http://www.netlib.org/blas/) installed on the system.
+    Then you have to guide the removal of the unoptimized version of
+    [**BLAS**](http://www.netlib.org/blas/) and guide it to the
+    installation of the library
+    [**OpenBLAS**](https://www.openblas.net/) through the most diverse
+    procedures depending on the GNU/Linux distribution used;
 
@@
 
-   - With the `rcompiler()` function you can build any version of [**R**](https://www.r-project.org/) into your computer architecture, which includes the most stable version of the language;
+-   With the `rcompiler()` function you can build any version of
+    [**R**](https://www.r-project.org/) into your computer architecture,
+    which includes the most stable version of the language;
 
-   - What is the latest stable version of [**R**](https://www.r-project.org/)? Are you too lazy to go to the [**R**](https://www.r-project.org/) site? Run `ropenblas::last_version_r(major = NULL)`.
+-   What is the latest stable version of
+    [**R**](https://www.r-project.org/)? Are you too lazy to go to the
+    [**R**](https://www.r-project.org/) site? Run
+    `ropenblas::last_version_r(major = NULL)`.
 
@@
 
-You must install the following dependencies on your operating system (Linux):
+You must install the following dependencies on your operating system
+(Linux):
 
@@
 
-   2 - **GNU GCC Compiler (C and Fortran)**: The GNU Compiler Collection - C and Fortran frontends.
+2 - **GNU GCC Compiler (C and Fortran)**: The GNU Compiler Collection -
+C and Fortran frontends.
 
-Do not worry that you will be notified if any of these dependencies are not installed.
+Do not worry that you will be notified if any of these dependencies are
+not installed.
 
@@
 
-Installing the [**ropenblas**](https://prdm0.github.io/ropenblas/) library is easy and will require you to have installed the **devtools** package.
-This will allow you to install the [**ropenblas**](https://prdm0.github.io/ropenblas/) package directly from GitHub.
-To install, after installing the **devtools** package, do:
+Installing the [**ropenblas**](https://prdm0.github.io/ropenblas/)
+library is easy and will require you to have installed the **devtools**
+package. This will allow you to install the
+[**ropenblas**](https://prdm0.github.io/ropenblas/) package directly
+from GitHub. To install, after installing the **devtools** package, do:
 
-```
     remotes::install_github(repo = "prdm0/ropenblas", force = TRUE)
-```
 
@@
 
-```
     install.packages("ropenblas")
-```
 
@@
 
-The [**ropenblas**](https://prdm0.github.io/ropenblas/) package currently provides five functions: `ropenblas()`, `rcompiler()`, `last_version_openblas()`, `last_version_r()` and `link_again()`.
-First of all, do:
+The [**ropenblas**](https://prdm0.github.io/ropenblas/) package
+currently provides five functions: `ropenblas()`, `rcompiler()`,
+`last_version_openblas()`, `last_version_r()`, `link_again()` and
+`rnews()`. First of all, do:
 
-```
     library(ropenblas)
-```
 
@@
 
-Installing, compiling, and linking the [**OpenBLAS**](https://www.openblas.net/) version **0.3.13** library to the [**R**](https://www.r-project.org/) language:
+Installing, compiling, and linking the
+[**OpenBLAS**](https://www.openblas.net/) version **0.3.13** library to
+the [**R**](https://www.r-project.org/) language:
 
@@
 <!-- ``` -->
+
 <!-- extSoftVersion()["BLAS"] -->
+
 <!-- ``` -->
@@
 
-Given the higher version, the function will return the latest stable version of the [**R**](https://www.r-project.org/) language. See the following example:
+Given the higher version, the function will return the latest stable
+version of the [**R**](https://www.r-project.org/) language. See the
+following example:
 
@@
 
-The `last_version_openblas()` function automatically searches [**OpenBLAS**](https://www.openblas.net/) library versions in the official [**GitHub**](https://github.com/xianyi/OpenBLAS) project.
+The `last_version_openblas()` function automatically searches
+[**OpenBLAS**](https://www.openblas.net/) library versions in the
+official [**GitHub**](https://github.com/xianyi/OpenBLAS) project.
 
@@
 
-This function is responsible for compiling a version of the [**R**](https://www.r-project.org/) language.
-The `x` argument is the version of [**R**](https://www.r-project.org/) that you want to compile.
-For example, `x = "4.0.0"` will compile and link **R-4.0.0** version as the major version on your system.
-By default (`x = NULL`) will be compiled the latest stable version of the [**R**](https://www.r-project.org/).
+This function is responsible for compiling a version of the
+[**R**](https://www.r-project.org/) language. The `x` argument is the
+version of [**R**](https://www.r-project.org/) that you want to compile.
+For example, `x = "4.0.4"` will compile and link **R-4.0.4** version as
+the major version on your system. By default (`x = NULL`) will be
+compiled the latest stable version of the
+[**R**](https://www.r-project.org/).
 
-For example, to compile the latest stable version of the [**R**](https://www.r-project.org/) language, do:
+For example, to compile the latest stable version of the
+[**R**](https://www.r-project.org/) language, do:
 
@@
 
-Regardless of your GNU/Linux distribution and what version of [**R**](https://www.r-project.org/) is in your repositories, you can have the latest stable version of the [**R**](https://www.r-project.org/) language compiled into your computer architecture.
+Regardless of your GNU/Linux distribution and what version of
+[**R**](https://www.r-project.org/) is in your repositories, you can
+have the latest stable version of the
+[**R**](https://www.r-project.org/) language compiled into your computer
+architecture.
 
-You can use the `rcompiler()` function to compile different versions of [**R**](https://www.r-project.org/).
-For example, running `rcompiler(x = "3.6.3")` and `rcompiler()` will install versions 3.6.3 and 4.0.0 on its GNU/Linux distribution, respectively.
-If you are in version 4.0.0 of [**R**](https://www.r-project.org/) and run the code `rcompiler(x = "3.6.3")` again, the function will identify the existence of version 3.6.3 in the system and give you the option to use the binaries that were built in a previous compilation.
-This avoids unnecessarys compilations.
+You can use the `rcompiler()` function to compile different versions of
+[**R**](https://www.r-project.org/). For example, running
+`rcompiler(x = "3.6.3")` and `rcompiler()` will install versions 3.6.3
+and 4.0.0 on its GNU/Linux distribution, respectively. If you are in
+version 4.0.0 of [**R**](https://www.r-project.org/) and run the code
+`rcompiler(x = "3.6.3")` again, the function will identify the existence
+of version 3.6.3 in the system and give you the option to use the
+binaries that were built in a previous compilation. This avoids
+unnecessarys compilations.
 
@@
 <!--    ``` -->
+
 <!--    ./configure --prefix=/opt/R/version_r --enable-memory-profiling --enable-R-shlib --enable-threads=posix -->
+
 <!--    --with-blas="-L/opt/OpenBLAS/lib -I/opt/OpenBLAS/include -lpthread -lm" -->
+
 <!--    ``` -->
@@
 -->
+
 <!-- Installing [**R**](https://www.r-project.org/) in the `/opt/R/version_r` directory is important because some functions in the package require this.
@@
 <!--    ``` -->
+
 <!--     ./configure --with-blas="..." complementary_flags -->
+
 <!--    ``` -->
@@
 
-The `link_again` function links again the [**OpenBLAS**](https://www.openblas.net/) library with the [**R**](https://www.r-project.org/) language, being useful to correct problems of untying the [**OpenBLAS**](https://www.openblas.net/) library that is common when the operating system is updated.
+The `link_again` function links again the
+[**OpenBLAS**](https://www.openblas.net/) library with the
+[**R**](https://www.r-project.org/) language, being useful to correct
+problems of untying the [**OpenBLAS**](https://www.openblas.net/)
+library that is common when the operating system is updated.
 
-The function `link_again` be able to link again the [**R**](https://www.r-project.org/) language with the [**OpenBLAS**](https://www.openblas.net/) library.
-Thus, link_again will only make the relinkagem when in some previous section of
-[**R**](https://www.r-project.org/) the ropenblas function has been used for the initial binding of the [**R**](https://www.r-project.org/) language with the [**OpenBLAS**](https://www.openblas.net/) library.
+The function `link_again` be able to link again the
+[**R**](https://www.r-project.org/) language with the
+[**OpenBLAS**](https://www.openblas.net/) library. Thus, link_again will
+only make the relinkagem when in some previous section of
+[**R**](https://www.r-project.org/) the ropenblas function has been used
+for the initial binding of the [**R**](https://www.r-project.org/)
+language with the [**OpenBLAS**](https://www.openblas.net/) library.
 
-For example, to relink the [**OpenBLAS**](https://www.openblas.net/) library with the [**R**](https://www.r-project.org/) language, do:
+For example, to relink the [**OpenBLAS**](https://www.openblas.net/)
+library with the [**R**](https://www.r-project.org/) language, do:
 
@@
 
-If `restart_r = TRUE` (default), a new section of [**R**](https://www.r-project.org/) is started after linking the [**OpenBLAS**](https://www.openblas.net/) library.
+If `restart_r = TRUE` (default), a new section of
+[**R**](https://www.r-project.org/) is started after linking the
+[**OpenBLAS**](https://www.openblas.net/) library.
 
-In situations where there was a disconnection due to an update of the operating system, the `ropenblas` function can be used to
-relink the [**OpenBLAS**](https://www.openblas.net/) library with the [**R**](https://www.r-project.org/) language, however, it will be necessary to compile the [**OpenBLAS**](https://www.openblas.net/) library again.
-If you are interested in recompiling the
-[**OpenBLAS**](https://www.openblas.net/) library and linking with [**R**](https://www.r-project.org/), use the `ropenblas` function.
-If the interest is to take advantage of a previous compilation of the [**OpenBLAS**](https://www.openblas.net/) library, the
-function `link_again` may be useful.
+In situations where there was a disconnection due to an update of the
+operating system, the `ropenblas` function can be used to relink the
+[**OpenBLAS**](https://www.openblas.net/) library with the
+[**R**](https://www.r-project.org/) language, however, it will be
+necessary to compile the [**OpenBLAS**](https://www.openblas.net/)
+library again. If you are interested in recompiling the
+[**OpenBLAS**](https://www.openblas.net/) library and linking with
+[**R**](https://www.r-project.org/), use the `ropenblas` function. If
+the interest is to take advantage of a previous compilation of the
+[**OpenBLAS**](https://www.openblas.net/) library, the function
+`link_again` may be useful.
 
@@
 
-Returns the contents of the [**NEWS.html**](https://cran.r-project.org/doc/manuals/r-release/NEWS.html) file in the standard browser installed on the operating system.
-The [**NEWS.html**](https://cran.r-project.org/doc/manuals/r-release/NEWS.html) file contains the main changes from the recently released versions of the [**R**](https://www.r-project.org/) language.
-The goal is to facilitate the query by invoking it directly from the [**R**](https://www.r-project.org/) command prompt.
-The rnews function is analogous to the news function of the utils package.
-However, using the news command in a terminal style bash shell is possible to receive a message like:
+Returns the contents of the
+[**NEWS.html**](https://cran.r-project.org/doc/manuals/r-release/NEWS.html)
+file in the standard browser installed on the operating system. The
+[**NEWS.html**](https://cran.r-project.org/doc/manuals/r-release/NEWS.html)
+file contains the main changes from the recently released versions of
+the [**R**](https://www.r-project.org/) language. The goal is to
+facilitate the query by invoking it directly from the
+[**R**](https://www.r-project.org/) command prompt. The rnews function
+is analogous to the news function of the utils package. However, using
+the news command in a terminal style bash shell is possible to receive a
+message like:
 
-```
     > news()
@@
     Error in browseURL(url) : 'browser' must be a non-empty character string
-```
 
-If `pdf = FALSE` (default), the [**NEWS.html**](https://cran.r-project.org/doc/manuals/r-release/NEWS.html) file will open in the browser, otherwise [**NEWS.pdf**](https://cran.r-project.org/doc/manuals/r-release/NEWS.pdf) will be opened.
-If `dev = FALSE` (default), it will not show changes made to the language development version.
-To see changes in the development version, do `dev = TRUE`.
+If `pdf = FALSE` (default), the
+[**NEWS.html**](https://cran.r-project.org/doc/manuals/r-release/NEWS.html)
+file will open in the browser, otherwise
+[**NEWS.pdf**](https://cran.r-project.org/doc/manuals/r-release/NEWS.pdf)
+will be opened. If `dev = FALSE` (default), it will not show changes
+made to the language development version. To see changes in the
+development version, do `dev = TRUE`.

### 2021-03-08 paper/paper.Rmd
Update paper

@@
 
-The `ropenblas` package aims to facilitate the daily life of R programmers on GNU/Linux systems without removing the possibility of specifying configurations that they deem convenient.
-Through the `ropenblas()` and `rcompiler()` functions, the package user will be able to compile and link the R language in his GNU/Linux distribution and link it to the OpenBLAS library, all within R and in a very simple way.
-All functions work without being influenced by the GNU/Linux distribution and its repositories, that is, it doesn't matter which GNU/Linux distribution is being used.
-Linking to the OpenBLAS library to R will bring a better computational performance of the language in the most diverse algebraic operations that are commonly used in areas such as statistics, data science and machine learning.
+The `ropenblas` package aims to facilitate the day-to-day life of R programmers who want a little more performance on GNU/Linux systems, without removing the possibility that specific configurations are made, if they deem convenient.
+Through the package's `ropenblas()` and `rcompiler()` functions, the library user will be able to compile and link the R language in his GNU/Linux distribution with the OpenBLAS library, all within R and in a very simple.
+All functions work without being influenced by the GNU/Linux distribution and are independent of their repositories, that is, it does not matter which GNU/Linux distribution is being used.
+Linking the OpenBLAS library to R will bring better computational performance to the language in the most diverse algebraic operations commonly used in areas such as statistics, data science and machine learning.
 
@@
 This will allow several researches in the areas of statistics, data science and machine learning to take advantage of a more efficient performance in algebraic calculations, for example, multiplication, factorization and matrix inversion.
-The `ropenblas` library, version 0.2.8 will also allow the R programmer to have, in his GNU/Linux distribution, several compiled versions of the R language giving the possibility to easily switch between these versions, this being an Open Source functionality that is only possible in some commercial IDEs of R.
+The `ropenblas` library, version 0.2.9 will also allow the R programmer to have, in his GNU/Linux distribution, several compiled versions of the R language giving the possibility to easily switch between these versions, this being an Open Source functionality that is only possible in some commercial IDEs of R.
 All this is done within the R language, minimizing the chance of less experienced users to break their operating system by running several instructions that are not perfectly understood.
@@
 Everything is done in a safe way, a since the `ropenblas` package uses the stable versions of the official development repositories of the OpenBLAS library and the R programming language, respectively.
-Until the present version, the package has more than 6600 downloads, having an average of more than 820 downloads in the month prior to the date of this submission, based on the official R language repositories.
+Until the present version, the package has more than 1000 downloads, having an average of more than 1000 downloads in the month prior to the date of this submission, based on the official R language repositories.
 
@@
 
-<!-- The `ropenblas` package is already available on the Comprehensive R Archive Network - CRAN, currently in version 0.2.8 and the project is maintained on GitHub at  <https://github.com/prdm0/ropenblas> where contributors can find others details of the code, information, as well as being able to contribute with the development of the project.
+The `ropenblas` package is already available on the Comprehensive R Archive Network - CRAN, currently in version 0.2.9 and the project is maintained on GitHub at <https://github.com/prdm0/ropenblas> where contributors can find others details of the code, information, as well as being able to contribute with the development of the project.
 Information can also be found on the project website.
@@
 Suggestions for improvements and bug reports can be sent via the link <https://github.com/prdm0/ropenblas/issues>.
--->
+You can find out how to contribute to the package by accessing the `CONTRIBUTING.md` file at <https://github.com/prdm0/ropenblas/blob/master/CONTRIBUTING.md>
 
-<!-- ```{r logo, echo = FALSE, message = FALSE, fig.cap = "Computer library logo.", fig.align = "center", out.width="30%"} -->
-<!-- knitr::include_graphics(path = "logo_ropenblas.png") -->
-<!-- ``` -->
+```{r logo, echo = FALSE, message = FALSE, fig.cap = "Computer library logo.", fig.align = "center", out.width="30%"}
+
+knitr::include_graphics(path = "logo.png")
+
+```
 
@@
 <!--   1. **GNU Make**: GNU Make utility to maintain groups of programs;  -->
+
 <!--   2. **GNU GCC Compiler (C and Fortran)**: The GNU Compiler Collection - C and Fortran frontends. -->
@@
 <!--   1. `install.packages("ropenblas")`: for installing the package available at CRAN; -->
+
 <!--   2. `devtools::install_github(repo = "prdm0/ropenblas, ref = "master", force = TRUE)`: for installing the package from the project development directory on GitHub. -->
@@
 <!-- ```{r packages, echo=FALSE, cache=TRUE} -->
+
 <!-- library("ropenblas") -->
+
 <!-- ``` -->
@@
 <!-- ```{r, prompt=TRUE, dependson="ropenblas", cache=TRUE, eval=FALSE} -->
+
 <!-- last_version_r(major = 4L) -->
+
 <!-- ``` -->
@@
 <!-- ```{r, dependson="ropenblas", cache=TRUE, prompt=TRUE} -->
+
 <!-- last_version_r(major = NULL) -->
+
 <!-- ``` -->
@@
 <!-- ```{r, dependson="ropenblas", cache=TRUE, prompt=TRUE} -->
+
 <!-- last_version_openblas() -->
+
 <!-- ``` -->
@@
 The x argument is the version of R that you want to compile.
-For example, `x = "4.0.2"` will compile and link R-4.0.2 version as the major version on your system.
+For example, `x = "4.0.4"` will compile and link R-4.0.4 version as the major version on your system.
 By default (`x = NULL`) will be compiled the latest stable version of the R.
@@
 <!-- ```{r, echo=FALSE, message=FALSE, warning=FALSE, fig.align='center', fig.cap="Window for entering the system administration password.", out.width="55%"} -->
+
 <!-- knitr::include_graphics("root.png") -->
+
 <!-- ``` -->
@@
 A list valid of the latest language versions can be obtained using the `last_version_r()` function.
-You can move to ``x` any of the returned versions.
+You can move to `x` any of the returned versions.
 This is the best way to choose a valid argument for `x`.
@@
 
-<!-- If the goal is to install the R language, switch between versions of R, and link the installed versions of the language with the OpenBLAS library, you shouldn't have to worry about the `with_blas` and `complementary_flags` arguments, respectively.
+If the goal is to install the R language, switch between versions of R, and link the installed versions of the language with the OpenBLAS library, you shouldn't have to worry about the `with_blas` and `complementary_flags` arguments, respectively.
 These arguments are useful for a minority of programmers who feel very specific needs to pass complementary flags to be considered in the R language compilation process, inclusion of complementary library directories, among other arguments that can be found in the official language manuals.
-By default, if nothing is passed to the `with_blas` and `complementary_flags` arguments, the compilation will be performed as follows: -->
+By default, if nothing is passed to the `with_blas` and `complementary_flags` arguments, the compilation will be performed as follows:
 
-<!-- ```{bash, eval=FALSE} -->
-<!-- ./configure --prefix=/opt/R/version_r --enable-memory-profiling  -->
-<!-- --enable-R-shlib --enable-threads=posix  -->
-<!-- --with-blas="-L/opt/OpenBLAS/lib -I/opt/OpenBLAS/include -->
-<!-- -lpthread -lm" -->
-<!-- ``` -->
+```{bash, eval=FALSE}
+./configure --prefix=/opt/R/version_r --enable-memory-profiling
+--enable-R-shlib --enable-threads=posix
+--with-blas="-L/opt/OpenBLAS/lib -I/opt/OpenBLAS/include -lpthread -lm"
+```
 
-<!-- As a suggestion and if you want to use the complementary arguments, that is, use `with_blas` and `complementary_flags`, do not change the directory `include` and `lib` of the OpenBLAS library in argument `with_blas`, considering that the `rcompiler()` function will always install the OpenBLAS library in the `/opt/OpenBLAS` directory, thus avoiding problems with breaking important links on your system and in the configuration of the initial version of R.
+As a suggestion and if you want to use the complementary arguments, that is, use `with_blas` and `complementary_flags`, do not change the directory `include` and `lib` of the OpenBLAS library in argument `with_blas`, considering that the `rcompiler()` function will always install the OpenBLAS library in the `/opt/OpenBLAS` directory, thus avoiding problems with breaking important links on your system and in the configuration of the initial version of R.
 If you try to pass a different installation directory to the OpenBLAS library, the `rcompiler()` function will disregard this installation of OpenBLAS and perform a safe installation in the `/opt/OpenBLAS` directory.
@@
 This allows no errors to be made and unforeseen bugs to occur.
-If there are reasons to consider complementary strings for the arguments `with_blas` and `complementary_flags`, the R language will be compiled as follows: -->
+If there are reasons to consider complementary strings for the arguments `with_blas` and `complementary_flags`, the R language will be compiled as follows:
 
-<!-- ```{bash, eval=FALSE} -->
-<!-- --prefix=/opt/R/version_r --enable-memory-profiling --enable-R-shlib -->
-<!-- --enable-threads=posix --with-blas="..." complementary_flags -->
-<!-- ``` -->
+```{bash, eval=FALSE}
+--prefix=/opt/R/version_r --enable-memory-profiling --enable-R-shlib
+--enable-threads=posix --with-blas="..." complementary_flags
+```
 
-<!-- The `rcompiler()` function will also avoid unnecessary compilations.
+The `rcompiler()` function will also avoid unnecessary compilations.
 Therefore, if your initial version of R is already linked to some version of the OpenBLAS library, only the R language will be compiled, with no need to compile the OpenBLAS library.
@@
 Below I will exemplify some situations in which the use of the `rcompiler()` function may be convenient.
--->
 
@@
 <!-- ```{r, eval=FALSE, prompt=TRUE} -->
+
 <!-- rcompiler(x = "4.0.2") # or simply rcompiler () or rcompiler (x = NULL) -->
+
 <!-- ``` -->
@@
 <!-- ```{r, prompt=TRUE} -->
+
 <!-- extSoftVersion()["BLAS"] -->
+
 <!-- ``` -->
@@
 <!-- ```{r, prompt=TRUE} -->
+
 <!-- sessionInfo() -->
+
 <!-- ``` -->
@@
 <!-- ```{r, eval=FALSE, prompt=TRUE} -->
+
 <!-- # First installation of R performed by the rcompiler() function: -->
+
 <!-- rcompiler(x = "4.0.0")  -->
+
 <!-- # Second installation of R performed by the rcompiler() function: -->
+
 <!-- rcompiler(x = "3.6.3") -->
+
 <!-- # Returning version 4.0.0 from R: -->
+
 <!-- rcompiler(x = "4.0.0") -->
+
 <!-- ``` -->
@@
 <!-- ```{r, eval=FALSE} -->
+
 <!-- rcompiler(x = "4.0.0") -->
+
 <!-- ``` -->
@@
 Suggestion of switching between versions of R without the need to recompile the language.", out.width="100%"} -->
+
 <!-- knitr::include_graphics("linkar_again.png") -->
+
 <!-- ``` -->
@@
 <!-- ```{r, eval=FALSE, prompt=FALSE} -->
+
 <!-- rcompiler(x = "3.0.0") -->
+
 <!-- ``` -->
@@
 <!-- ```{r, echo=FALSE, message=FALSE, warning=FALSE, fig.align='center', fig.cap="Attempted to install an R language version prior to version 3.1.0.", out.width="100%"} -->
+
 <!-- knitr::include_graphics("attention.png") -->
+
 <!-- ``` -->
@@
 <!-- ```{r, eval=FALSE, prompt=TRUE} -->
+
 <!-- ropenblas() -->
+
 <!-- ``` -->
@@
 <!-- ```{r, echo=FALSE, message=FALSE, warning=FALSE, fig.align='center', fig.cap="Output informing the end of the procedure for linking the OpenBLAS library to the R language.", out.width="100%"} -->
+
 <!-- knitr::include_graphics("ropenblas_01.png") -->
+
 <!-- ``` -->
@@
 <!-- ```{r, eval=FALSE, prompt=TRUE} -->
+
 <!-- ropenblas("0.3.8") -->
+
 <!-- ``` -->
@@
 <!-- ```{r, echo=FALSE, message=FALSE, warning=FALSE, fig.align='center', fig.cap="Asking if the user really wants to compile and link an older version of the OpenBLAS library.", out.width="100%"} -->
+
 <!-- knitr::include_graphics("ropenblas_02.png") -->
+
 <!-- ``` -->
 
-<!-- The code below is a small example of the benefits of considering linking the R language to the OpenBLAS library, in which singular-value decomposition of a rectangular matrix is computed, codes that are executed on the same machine, version of R and section.
+The code below is a small example of the benefits of considering linking the R language to the OpenBLAS library, in which singular-value decomposition of a rectangular matrix is computed, codes that are executed on the same machine, version of R and section.
 The first part of the code was executed with R without being linked to a version of the OpenBLAS library and the second part was executed after using the `ropenblas()` function.
-Note that the code when executed in R linked to a version of the OpenBLAS library can be clearly more efficient: -->
+Note that the code when executed in R linked to a version of the OpenBLAS library can be clearly more efficient:
 
-<!-- ```{r, eval = FALSE} -->
-<!-- # Using the BLAS + Lapack library: -->
-<!-- # Matrix products: default -->
-<!-- # BLAS:   /usr/lib/libblas.so.3.9.0 -->
-<!-- # LAPACK: /usr/lib/liblapack.so.3.9.0 -->
-<!-- n <- 1e3L -->
-<!-- X <- matrix(rnorm(n * n), n, n) -->
-<!-- system.time(svd(X))  -->
-<!-- ## user      system      elapsed -->
-<!-- ## 7.246     0.029       7.286  -->
+```{r, eval = FALSE}
 
-<!-- # ---- -->
+# Using the BLAS + Lapack library:
 
-<!-- # After linking the OpenBLAS library to R using the ropenblas() function: -->
-<!-- # Using the OpenBLAS version 0.3.10 library: -->
-<!-- # Matrix products: default -->
-<!-- # BLAS/LAPACK: /opt/OpenBLAS/lib/libopenblas_haswellp-r0.3.10.so -->
-<!-- n <- 1e3L -->
-<!-- X <- matrix(rnorm(n * n), n, n) -->
-<!-- system.time(svd(X))  -->
-<!-- ## user      system    elapsed -->
-<!-- ## 3.024     2.004     0.677  -->
-<!-- ``` -->
+# Matrix products: default
+
+# BLAS:   /usr/lib/libblas.so.3.9.0
+
+# LAPACK: /usr/lib/liblapack.so.3.9.0
+
+n <- 1e3L
+
+X <- matrix(rnorm(n * n), n, n)
+
+system.time(svd(X))
+
+## user      system      elapsed
+
+## 7.246     0.029       7.286
+
+# ----
+
+# After linking the OpenBLAS library to R using the ropenblas() function:
+
+# Using the OpenBLAS version 0.3.13 library:
+
+# Matrix products: default
+
+# BLAS/LAPACK: /opt/OpenBLAS/lib/libopenblas_haswellp-r0.3.13.so
+
+n <- 1e3L
+
+X <- matrix(rnorm(n * n), n, n)
+
+system.time(svd(X))
+
+## user      system    elapsed
+
+## 3.024     2.004     0.677
+
+```
+
+Through a banchmark it is possible to better understand the performance gain that can be achieved by linking the R language to the OpenBLAS library.
+Figure 2 presents the banchmarks in the form of violin plot, in which 100 reproductions of the `svd(X)` expression were considered, in the form of the code above, with the R linked to the BLAS library and linked to the OpenBLAS library, respectively, on the same hardware.
+It was observed that the average time of execution of the routine `svd(X)` considering the OpenBLAS library was less than 10 times the time necessary to execute it in R linking to a non-optimized version of BLAS, being the average time of 0.64 and 6.52 seconds, respectively.
+
+```{r bench, echo = FALSE, fig.cap = "Benchmarks of a Singular Value Decomposition of a Matrix.", fig.align = "center", out.width="60%"}
+knitr::include_graphics(path = "benchmark.png") 
+```
 
@@
 
-<!-- Thus, `link_again()` will only make the relinkagem when in some previous section of R the `ropenblas()` function has been used for the initial binding of the R language with the OpenBLAS library.
--->
+Thus, `link_again()` will only make the relinkagem when in some previous section of R the `ropenblas()` function has been used for the initial binding of the R language with the OpenBLAS library.
 
-<!-- The use of the function is quite simple, just by running the code `link_again()`, since the function has no arguments.
+The use of the function is quite simple, just by running the code `link_again()`, since the function has no arguments.
 It will automatically detect if there was a link break that will be rebuilt again without the need for any compilation.
@@
 Link breakage rarely occurs, but if it does, it can be resolved quickly.
-The following code and image exemplify a possible reconstruction of symbolic links using the `link_again()` function: -->
+The following code and image exemplify a possible reconstruction of symbolic links using the `link_again()` function:
 
@@
 <!-- ```{r, echo=FALSE, message=FALSE, warning=FALSE, fig.align='center', fig.cap="If an unlinking of the OpenBLAS library occurs, the function will re-link the library.", out.width="100%"} -->
+
 <!-- knitr::include_graphics("link_again_01.png") -->
+
 <!-- ``` -->
@@
 <!-- ```{r, echo=FALSE, message=FALSE, warning=FALSE, fig.align='center', fig.cap="If relinking is not required, the function will make it clear.", out.width="100%"} -->
+
 <!-- knitr::include_graphics("link_again_02.png") -->
+
 <!-- ``` -->
@@
 <!-- ```{r, eval=FALSE} -->
+
 <!-- news() -->
+
 <!-- ## starting httpd help server ... done -->
+
 <!-- ## Error in browseURL(url): 'browser' must be a non-empty character string -->
+
 <!-- ``` -->

### 2021-03-08 paper/simple_benchmark.R

@@ -1,0 +1,37 @@
+library(magrittr)
+library(tibble)
+library(ggplot2)
+library(dplyr)
+
+# n <- 1e3L
+# X <- matrix(rnorm(n * n), n, n)
+# 
+# result_openblas <- microbenchmark::microbenchmark(svd(X), unit = "s") %>% 
+#   as_tibble() %>% 
+#   mutate(time = time / 1e9)
+# result_openblas[, 1L] <- "Using OpenBLAS"
+# 
+# save(file = "/home/prdm0/Downloads/ropenblas/paper/result_openblas.RData", result_openblas)
+
+# Plot Benchmarck
+
+load(file = "result_blas.RData")
+load(file = "result_openblas.RData")
+
+result <- rbind(result_blas, result_openblas)
+
+p <- ggplot(result, aes(x = expr, y = time))
+
+p <- 
+  p + geom_violin() + 
+  xlab("Librarys") +
+  ylab("Time in seconds") + 
+  ggtitle("Singular Value Decomposition of a Matrix") +
+  theme(
+    plot.title = element_text(face = "bold"),
+    axis.title = element_text(face = "bold"),
+    axis.text.x.top = element_text(face = "bold")
+  )
+
+ggsave(filename = "/home/prdm0/Downloads/ropenblas/paper/benchmark.png")
+

### 2021-03-09 paper/paper.Rmd
Update paper
Update

@@
 All functions work without being influenced by the GNU/Linux distribution and are independent of their repositories, that is, it does not matter which GNU/Linux distribution is being used.
-Linking the OpenBLAS library to R will bring better computational performance to the language in the most diverse algebraic operations commonly used in areas such as statistics, data science and machine learning.
+Linking the OpenBLAS library to R will bring better computational performance to the language in the most diverse algebraic operations commonly used in areas such as statistics, data science, and machine learning.
 
@@
 The `ropenblas` package aims to allow algebraic computing of R to be performed using the OpenBLAS library, that is, it allows easy linking of R to the OpenBLAS library on GNU/Linux systems without depending on the distribution repositories.
-This will allow several researches in the areas of statistics, data science and machine learning to take advantage of a more efficient performance in algebraic calculations, for example, multiplication, factorization and matrix inversion.
+This will allow several researches in the areas of statistics, data science, and machine learning to take advantage of more efficient performance in algebraic calculations, for example, multiplication, factorization, and matrix inversion.
 The `ropenblas` library, version 0.2.9 will also allow the R programmer to have, in his GNU/Linux distribution, several compiled versions of the R language giving the possibility to easily switch between these versions, this being an Open Source functionality that is only possible in some commercial IDEs of R.
@@
 The fact that the `ropenblas` package does not depend on the repositories of the GNU/Linux distribution will allow that in more stable distributions the R programmer will have at his disposal the most recent version of the OpenBLAS libraries and the R language.
-Everything is done in a safe way, a since the `ropenblas` package uses the stable versions of the official development repositories of the OpenBLAS library and the R programming language, respectively.
-Until the present version, the package has more than 1000 downloads, having an average of more than 1000 downloads in the month prior to the date of this submission, based on the official R language repositories.
+Everything is done safely, since the `ropenblas` package uses the stable versions of the official development repositories of the OpenBLAS library and the R programming language, respectively.
+Until the present version, the package has more than 1000 downloads, having an average of more than 1000 downloads in the month before the date of this submission, based on the official R language repositories.
 
@@
 
-The `ropenblas` package is already available on the Comprehensive R Archive Network - CRAN, currently in version 0.2.9 and the project is maintained on GitHub at <https://github.com/prdm0/ropenblas> where contributors can find others details of the code, information, as well as being able to contribute with the development of the project.
+1.  Everything is done within the R language;
+2.  The procedure (use of functions) will be the same for any Linux distribution;
+3.  The OpenBLAS library will be compiled and you will choose which build version to bind to R, regardless of your Linux distribution;
+4.  The package allows you to install R $\geq 3.1.0$, also allowing you to install one more version, in addition to allowing you to easily switch between those versions;
+5.
+The linked versions of R will continue to be recognized by their Integrated Development Environment - IDE and nothing will have to be adjusted in your GNU/Linux distribution after using any function of the package;
+6.  Unnecessary builds will be avoided. Therefore, if you need to switch between compiled versions of the R language, the use of binaries compiled in previous times will be suggested;
+7.  If any errors occur, the functions of the package will not damage the previous installation of the language;
+8.  If something better can be done or if a newer version of what you want to install (R or OpenBLAS) exists, the functions will automatically suggest that you consider installing newer versions.
+
+The `ropenblas` package is already available on the Comprehensive R Archive Network - CRAN, currently in version 0.2.9, and the project is maintained on GitHub at <https://github.com/prdm0/ropenblas> where contributors can find other details of the code, information, as well as being able to contribute with the development of the project.
 Information can also be found on the project website.
-On the website it is also possible to read the `NEWS.md` file with details of the versions and the focus of the current development.
+On the website, it is also possible to read the `NEWS.md` file with details of the versions and the focus of the current development.
 The site is deposited at <https://prdm0.github.io/ropenblas/>.
 Suggestions for improvements and bug reports can be sent via the link <https://github.com/prdm0/ropenblas/issues>.
-You can find out how to contribute to the package by accessing the `CONTRIBUTING.md` file at <https://github.com/prdm0/ropenblas/blob/master/CONTRIBUTING.md>
+You can find out how to contribute to the package by accessing the `CONTRIBUTING.md` file at <https://github.com/prdm0/ropenblas/blob/master/CONTRIBUTING.md>.
 
@@
 -->
-
-1.  Everything is done within the R language;
-2.  The procedure (use of functions) will be the same for any Linux distribution;
-3.  The OpenBLAS library will be compiled and you will choose which build version to bind to R, regardless of your Linux distribution;
-4.  The package allows you to install R $\geq 3.1.0$, also allowing you to install one more version, in addition to allowing you to easily switch between those versions;
-5.
-The linked versions of R will continue to be recognized by their Integrated Development Environment - IDE and nothing will have to be adjusted in your GNU/Linux distribution after using any function of the package;
-6.  Unnecessary builds will be avoided. Therefore, if you need to switch between compiled versions of the R language, the use of binaries compiled in previous times will be suggested;
-7.  If any errors occur, the functions of the package will not damage the previous installation of the language;
-8.  If something better can be done or if a newer version of what you want to install (R or OpenBLAS) exists, the functions will automatically suggest that you consider installing newer versions.
 
@@
 The `ropenblas` library exports six functions for use which are the `rcompiler()`, `ropenblas()`, `last_version_r()`, `last_version_openblas()`, `link_again()` and `rnews()`.
-All of them are very simple to use and have few arguments that are sufficient to maintain flexibility of use.
+All of them are very simple to use and have few arguments that are sufficient to maintain the flexibility of use.
 Any example that follows will consider that the installation of the `ropenblas` package has been carried out and the package has been loaded (`library(ropenblas)`).
-In addition, functions like `rcompiler()` and `ropenblas()` do not return content or data structures that are of any practical use.
-What these functions do is configure the GNU/Linux system to use R, configure different versions of the language, switch between versions and link with the OpenBLAS library.
+Also, functions like `rcompiler()` and `ropenblas()` do not return content or data structures that are of any practical use.
+What these functions do is configure the GNU/Linux system to use R, configure different versions of the language, switch between versions, and link with the OpenBLAS library.
 It is also possible to obtain a summary of the versions of R and the OpenBLAS library that are available.
@@
 The function `last_version_r()` automatically searches, in the official repositories of language R, for information about versions of language R.
-Its general use is `last_version_r(major = NULL)` , where the argument `major` indicates which is the largest version of R that you want to search for the version list.
-Therefore, for the argument `major` a number must be passed, preferably an integer that indicates which is the largest version to be considered.
+Its general use is `last_version_r(major = NULL)`, where the argument major indicates which is the largest version of R that you want to search for the version list.
+Therefore, for argument `major`, a number must be passed, preferably an integer that indicates which is the largest version to be considered.
 
@@
 
-The `last_version_openblas()` function works similarly to the `last_version_r()` function, returning a list of three elements named in the same way with the information from the latest version, all the versions and the number of versions of the OpenBLAS library, respectively.
+The `last_version_openblas()` function works similarly to the `last_version_r()` function, returning a list of three elements named in the same way with the information from the latest version, all the versions, and the number of versions of the OpenBLAS library, respectively.
 
@@
 The x argument is the version of R that you want to compile.
-For example, `x = "4.0.4"` will compile and link R-4.0.4 version as the major version on your system.
+For example, `x = "4.0.4"` will compile and link the R-4.0.4 version as the major version on your system.
 By default (`x = NULL`) will be compiled the latest stable version of the R.
@@
 If the goal is to install the R language, switch between versions of R, and link the installed versions of the language with the OpenBLAS library, you shouldn't have to worry about the `with_blas` and `complementary_flags` arguments, respectively.
-These arguments are useful for a minority of programmers who feel very specific needs to pass complementary flags to be considered in the R language compilation process, inclusion of complementary library directories, among other arguments that can be found in the official language manuals.
+These arguments are useful for a minority of programmers who feel very specific needs to pass complementary flags to be considered in the R language compilation process, the inclusion of complementary library directories, among other arguments that can be found in the official language manuals.
 By default, if nothing is passed to the `with_blas` and `complementary_flags` arguments, the compilation will be performed as follows:
@@
 
--   `x`: String with the version of the OpenBLAS library to be compiled, installed and linked with the main R installation (by default it is considered the latest version);
--   `restart_r`: Logical value (default `restart_r = TRUE`) to update the R section after compiling, installing and linking the OpenBLAS library.
+-   `x`: String with the version of the OpenBLAS library to be compiled, installed, and linked with the main R installation (by default it is considered the latest version);
+-   `restart_r`: Logical value (default `restart_r = TRUE`) to update the R section after compiling, installing, and linking the OpenBLAS library.
 
@@
 
-The code below is a small example of the benefits of considering linking the R language to the OpenBLAS library, in which singular-value decomposition of a rectangular matrix is computed, codes that are executed on the same machine, version of R and section.
+The code below is a small example of the benefits of considering linking the R language to the OpenBLAS library, in which singular-value decomposition of a rectangular matrix is computed, codes that are executed on the same machine, version of R, and section.
 The first part of the code was executed with R without being linked to a version of the OpenBLAS library and the second part was executed after using the `ropenblas()` function.
-Note that the code when executed in R linked to a version of the OpenBLAS library can be clearly more efficient:
+Note that the code when executed in R linked to a version of the OpenBLAS library can be more efficient:
 
@@
 
-Through a banchmark it is possible to better understand the performance gain that can be achieved by linking the R language to the OpenBLAS library.
-Figure 2 presents the banchmarks in the form of violin plot, in which 100 reproductions of the `svd(X)` expression were considered, in the form of the code above, with the R linked to the BLAS library and linked to the OpenBLAS library, respectively, on the same hardware.
+Through a benchmark it is possible to better understand the performance gain that can be achieved by linking the R language to the OpenBLAS library.
+Figure 2 presents the benchmarks in the form of a violin plot, in which 100 reproductions of the `svd(X)` expression were considered, in the form of the code above, with the R linked to the BLAS library and linked to the OpenBLAS library, respectively, on the same hardware.
 It was observed that the average time of execution of the routine `svd(X)` considering the OpenBLAS library was less than 10 times the time necessary to execute it in R linking to a non-optimized version of BLAS, being the average time of 0.64 and 6.52 seconds, respectively.
@@
 The `link_again()` function links again the OpenBLAS library with the R language, being useful to correct problems of untying the OpenBLAS library that is common when the operating system is updated.
-The function be able to link again the R language with the OpenBLAS library.
+The function can link again the R language with the OpenBLAS library.
 
-Thus, `link_again()` will only make the relinkagem when in some previous section of R the `ropenblas()` function has been used for the initial binding of the R language with the OpenBLAS library.
+Thus, `link_again()` will only make the linkage when in some previous section of R the `ropenblas()` function has been used for the initial binding of the R language with the OpenBLAS library.
 
-The use of the function is quite simple, just by running the code `link_again()`, since the function has no arguments.
+The use of the function is quite simple, just by running the code `link_again()` since the function has no arguments.
 It will automatically detect if there was a link break that will be rebuilt again without the need for any compilation.

### 2021-03-11 paper/paper.Rmd
Update

@@
 The `ropenblas` package aims to facilitate the day-to-day life of R programmers who want a little more performance on GNU/Linux systems, without removing the possibility that specific configurations are made, if they deem convenient.
-Through the package's `ropenblas()` and `rcompiler()` functions, the library user will be able to compile and link the R language in his GNU/Linux distribution with the OpenBLAS library, all within R and in a very simple.
+Through the package's `ropenblas()` and `rcompiler()` functions, the library user will be able to compile and link the R language in his GNU/Linux distribution with the OpenBLAS library, all within R and in a very simple fashion.
 All functions work without being influenced by the GNU/Linux distribution and are independent of their repositories, that is, it does not matter which GNU/Linux distribution is being used.
@@
 The `ropenblas` package aims to allow algebraic computing of R to be performed using the OpenBLAS library, that is, it allows easy linking of R to the OpenBLAS library on GNU/Linux systems without depending on the distribution repositories.
-This will allow several researches in the areas of statistics, data science, and machine learning to take advantage of more efficient performance in algebraic calculations, for example, multiplication, factorization, and matrix inversion.
+This will allow several researchers in the areas of statistics, data science, and machine learning to take advantage of more efficient performance in algebraic calculations, for example, multiplication, factorization, and matrix inversion.
 The `ropenblas` library, version 0.2.9 will also allow the R programmer to have, in his GNU/Linux distribution, several compiled versions of the R language giving the possibility to easily switch between these versions, this being an Open Source functionality that is only possible in some commercial IDEs of R.
@@
 Everything is done safely, since the `ropenblas` package uses the stable versions of the official development repositories of the OpenBLAS library and the R programming language, respectively.
-Until the present version, the package has more than 1000 downloads, having an average of more than 1000 downloads in the month before the date of this submission, based on the official R language repositories.
+Until the present version, the package has more than 11000 downloads, having an average of more than 1000 downloads in the month before the date of this submission, based on the official R language repositories.
 
@@
 The linked versions of R will continue to be recognized by their Integrated Development Environment - IDE and nothing will have to be adjusted in your GNU/Linux distribution after using any function of the package;
-6.  Unnecessary builds will be avoided. Therefore, if you need to switch between compiled versions of the R language, the use of binaries compiled in previous times will be suggested;
+6.  Unnecessary builds will be avoided. Therefore, if you need to switch between compiled versions of the R language, the use of binaries compiled compiled previously will be suggested;
 7.  If any errors occur, the functions of the package will not damage the previous installation of the language;
-8.  If something better can be done or if a newer version of what you want to install (R or OpenBLAS) exists, the functions will automatically suggest that you consider installing newer versions.
+8.
+If something better can be done or if a newer version of what you want to install (R or OpenBLAS) exists, the functions will automatically suggest that you should consider installing newer versions.
 
@@
 If the goal is to install the R language, switch between versions of R, and link the installed versions of the language with the OpenBLAS library, you shouldn't have to worry about the `with_blas` and `complementary_flags` arguments, respectively.
-These arguments are useful for a minority of programmers who feel very specific needs to pass complementary flags to be considered in the R language compilation process, the inclusion of complementary library directories, among other arguments that can be found in the official language manuals.
-By default, if nothing is passed to the `with_blas` and `complementary_flags` arguments, the compilation will be performed as follows:
+For more details, consult the `README.md` of the project or the official documentation of the package in [CRAN](https://cran.r-project.org/web/packages/ropenblas/ropenblas.pdf).
 
-```{bash, eval=FALSE}
-./configure --prefix=/opt/R/version_r --enable-memory-profiling
---enable-R-shlib --enable-threads=posix
---with-blas="-L/opt/OpenBLAS/lib -I/opt/OpenBLAS/include -lpthread -lm"
-```
+<!-- These arguments are useful for a minority of programmers who feel very specific needs to pass complementary flags to be considered in the R language compilation process, the inclusion of complementary library directories, among other arguments that can be found in the official language manuals.
+By default, if nothing is passed to the `with_blas` and `complementary_flags` arguments, the compilation will be performed as follows: -->
 
-As a suggestion and if you want to use the complementary arguments, that is, use `with_blas` and `complementary_flags`, do not change the directory `include` and `lib` of the OpenBLAS library in argument `with_blas`, considering that the `rcompiler()` function will always install the OpenBLAS library in the `/opt/OpenBLAS` directory, thus avoiding problems with breaking important links on your system and in the configuration of the initial version of R.
+<!-- ```{bash, eval=FALSE} -->
+
+<!-- ./configure --prefix=/opt/R/version_r --enable-memory-profiling -->
+
+<!-- --enable-R-shlib --enable-threads=posix -->
+
+<!-- --with-blas="-L/opt/OpenBLAS/lib -I/opt/OpenBLAS/include -lpthread -lm" -->
+
+<!-- ``` -->
+
+<!-- As a suggestion and if you want to use the complementary arguments, that is, use `with_blas` and `complementary_flags`, do not change the directory `include` and `lib` of the OpenBLAS library in argument `with_blas`, considering that the `rcompiler()` function will always install the OpenBLAS library in the `/opt/OpenBLAS` directory, thus avoiding problems with breaking important links on your system and in the configuration of the initial version of R.
 If you try to pass a different installation directory to the OpenBLAS library, the `rcompiler()` function will disregard this installation of OpenBLAS and perform a safe installation in the `/opt/OpenBLAS` directory.
@@
 This allows no errors to be made and unforeseen bugs to occur.
-If there are reasons to consider complementary strings for the arguments `with_blas` and `complementary_flags`, the R language will be compiled as follows:
+If there are reasons to consider complementary strings for the arguments `with_blas` and `complementary_flags`, the R language will be compiled as follows: -->
 
-```{bash, eval=FALSE}
---prefix=/opt/R/version_r --enable-memory-profiling --enable-R-shlib
---enable-threads=posix --with-blas="..." complementary_flags
-```
+<!-- ```{bash, eval=FALSE} -->
 
-The `rcompiler()` function will also avoid unnecessary compilations.
-Therefore, if your initial version of R is already linked to some version of the OpenBLAS library, only the R language will be compiled, with no need to compile the OpenBLAS library.
-Although the initial description of the `rcompiler()` function may seem a little complicated, its use is very simple.
+<!-- --prefix=/opt/R/version_r --enable-memory-profiling --enable-R-shlib -->
+
+<!-- --enable-threads=posix --with-blas="..." complementary_flags -->
+
+<!-- ``` -->
+
+<!-- Although the initial description of the `rcompiler()` function may seem a little complicated, its use is very simple.
 Below I will exemplify some situations in which the use of the `rcompiler()` function may be convenient.
+-->
 
@@
 
-The code below is a small example of the benefits of considering linking the R language to the OpenBLAS library, in which singular-value decomposition of a rectangular matrix is computed, codes that are executed on the same machine, version of R, and section.
-The first part of the code was executed with R without being linked to a version of the OpenBLAS library and the second part was executed after using the `ropenblas()` function.
-Note that the code when executed in R linked to a version of the OpenBLAS library can be more efficient:
+Table 1 below presents the benefit of considering an optimized version of BLAS.
+Computational costs are presented in the calculation of the singular decomposition in a rectangular matrix (function `svd()`) and in the calculation of the inverse of that same matrix (function `solve()`).
+Some repetitions (100 repetitions) of each of the respective functions were performed.
+The benchmark can be better observed through the violin plots shown in Figure 2.
 
-```{r, eval = FALSE}
+\
 
-# Using the BLAS + Lapack library:
-
-# Matrix products: default
-
-# BLAS:   /usr/lib/libblas.so.3.9.0
-
-# LAPACK: /usr/lib/liblapack.so.3.9.0
-
-n <- 1e3L
-
-X <- matrix(rnorm(n * n), n, n)
-
-system.time(svd(X))
-
-## user      system      elapsed
-
-## 7.246     0.029       7.286
-
-# ----
-
-# After linking the OpenBLAS library to R using the ropenblas() function:
-
-# Using the OpenBLAS version 0.3.13 library:
-
-# Matrix products: default
-
-# BLAS/LAPACK: /opt/OpenBLAS/lib/libopenblas_haswellp-r0.3.13.so
-
-n <- 1e3L
-
-X <- matrix(rnorm(n * n), n, n)
-
-system.time(svd(X))
-
-## user      system    elapsed
-
-## 3.024     2.004     0.677
-
-```
+| Functions  | Library  | Time (seconds) |
+|----------- |----------|:---------------:|
+| `svd(x)`   | BLAS     | 6.520      |
+| `svd(x)`   | OpenBLAS | 0.641     |
+| `solve(x)` | BLAS     | 1.640      |
+| `solve(x)` | OpenBLAS | 0.640      |
+: Comparison of the computational costs of the `svd()` and `solve()` functions.
 
@@
 
-```{r bench, echo = FALSE, fig.cap = "Benchmarks of a Singular Value Decomposition of a Matrix.", fig.align = "center", out.width="60%"}
+```{r bench, echo = FALSE, fig.cap = "Benchmarks of a decomposition of singular and inverse value of a matrix of dimension 1000 x 1000.", fig.align = "center", out.width="90%"}
 knitr::include_graphics(path = "benchmark.png") 

### 2021-03-11 paper/simple_benchmark.R

@@ -3,34 +3,41 @@ library(tibble)
 library(ggplot2)
 library(dplyr)
 
-# n <- 1e3L
-# X <- matrix(rnorm(n * n), n, n)
-# 
-# result_openblas <- microbenchmark::microbenchmark(svd(X), unit = "s") %>% 
-#   as_tibble() %>% 
-#   mutate(time = time / 1e9)
-# result_openblas[, 1L] <- "Using OpenBLAS"
-# 
-# save(file = "/home/prdm0/Downloads/ropenblas/paper/result_openblas.RData", result_openblas)
+n <- 1e3L
+set.seed(0)
+X <- matrix(rnorm(n * n), n, n)
+result_solve_openblas <- microbenchmark::microbenchmark(solve(X), unit = "s") %>%
+  as_tibble() %>%
+  mutate(time = time / 1e9)
+result_solve_openblas[, 1L] <- "Using OpenBLAS"
+
+save(file = "/home/prdm0/Downloads/ropenblas/paper/result_solve_openblas.RData", result_solve_openblas)
 
 # Plot Benchmarck
 
-load(file = "result_blas.RData")
-load(file = "result_openblas.RData")
+load(file = "/home/prdm0/Downloads/ropenblas/paper/result_blas.RData")
+load(file = "/home/prdm0/Downloads/ropenblas/paper/result_openblas.RData")
+load(file = "/home/prdm0/Downloads/ropenblas/paper/result_solve_blas.RData")
+load(file = "/home/prdm0/Downloads/ropenblas/paper/result_solve_openblas.RData")
 
-result <- rbind(result_blas, result_openblas)
 
-p <- ggplot(result, aes(x = expr, y = time))
+result <- rbind(result_blas, result_openblas, result_solve_blas, result_openblas)
+result[, 3] <- c(rep("svd", 200), rep("solve", 200)) 
+names(result) <- c("expr", "time", "Functions")
+
+p <- ggplot(result, aes(x = expr, y = time, fill=Functions))
 
 p <- 
   p + geom_violin() + 
   xlab("Librarys") +
   ylab("Time in seconds") + 
-  ggtitle("Singular Value Decomposition of a Matrix") +
+  ggtitle("Singular Value Decomposition\nInverse Function", 
+          subtitle = "svd and solve functions") +
   theme(
     plot.title = element_text(face = "bold"),
     axis.title = element_text(face = "bold"),
-    axis.text.x.top = element_text(face = "bold")
[…]

### 2021-03-11 paper/paper.Rmd
Update

@@
 
+# Improvements
+
+The package will continue to evolve and code reviews will always be carried out.
+In addition, contributions to the development of the package are always welcome, especially those that aim to allow the `rcompiler()` and `ropenblas()` functions to work on Windows systems.
+There is also an interest that the `ropenblas` package will allow the linking of the Intel Math Kernel Library - MKL, just as it is done with the OpenBLAS library.
+All of these are improvements that we would like to see in future versions of the package.
+
 # References

### 2021-03-11 paper/paper.Rmd
Update

@@
 Table 1 below presents the benefit of considering an optimized version of BLAS.
-Computational costs are presented in the calculation of the singular decomposition in a rectangular matrix (function `svd()`) and in the calculation of the inverse of that same matrix (function `solve()`).
+Computational costs are presented in the calculation of the singular decomposition in a rectangular matrix (`svd()`) and in the calculation of the inverse of that same matrix (`solve()` function).
 Some repetitions (100 repetitions) of each of the respective functions were performed.
@@
 | `solve(x)` | OpenBLAS | 0.640      |
-: Comparison of the computational costs of the `svd()` and `solve()` functions.
+: Comparison of the computational costs of the `svd()` and `solve()` functions (average of 100 repetitions).
 

### 2021-03-11 paper/paper.Rmd
Update

@@
 Table 1 below presents the benefit of considering an optimized version of BLAS.
-Computational costs are presented in the calculation of the singular decomposition in a rectangular matrix (`svd()`) and in the calculation of the inverse of that same matrix (`solve()` function).
+Computational costs are presented in the calculation of the singular decomposition in a rectangular matrix (`svd()` function) and in the calculation of the inverse of that same matrix (`solve()` function).
 Some repetitions (100 repetitions) of each of the respective functions were performed.

### 2021-03-19 paper/paper.Rmd
Update

@@
 
-# Statement of Need
+<!-- # Statement of Need -->
 
-The `ropenblas` package aims to allow algebraic computing of R to be performed using the OpenBLAS library, that is, it allows easy linking of R to the OpenBLAS library on GNU/Linux systems without depending on the distribution repositories.
+<!-- The `ropenblas` package aims to allow algebraic computing of R to be performed using the OpenBLAS library, that is, it allows easy linking of R to the OpenBLAS library on GNU/Linux systems without depending on the distribution repositories.
 This will allow several researchers in the areas of statistics, data science, and machine learning to take advantage of more efficient performance in algebraic calculations, for example, multiplication, factorization, and matrix inversion.
@@
 All this is done within the R language, minimizing the chance of less experienced users to break their operating system by running several instructions that are not perfectly understood.
+-->
 
-The fact that the `ropenblas` package does not depend on the repositories of the GNU/Linux distribution will allow that in more stable distributions the R programmer will have at his disposal the most recent version of the OpenBLAS libraries and the R language.
+<!-- The fact that the `ropenblas` package does not depend on the repositories of the GNU/Linux distribution will allow that in more stable distributions the R programmer will have at his disposal the most recent version of the OpenBLAS libraries and the R language.
 Everything is done safely, since the `ropenblas` package uses the stable versions of the official development repositories of the OpenBLAS library and the R programming language, respectively.
 Until the present version, the package has more than 11000 downloads, having an average of more than 1000 downloads in the month before the date of this submission, based on the official R language repositories.
+-->
 
@@
 
-The term "computational efficiency" is very common for those who program statistical methods, in which a large part of them involve algebraic operations that are often reproduced in computationally intensive simulations, such as Monte-Carlo simulations - MC and resampling methods, as is the case with bootstrap resampling.
+<!-- The term "computational efficiency" is very common for those who program statistical methods, in which a large part of them involve algebraic operations that are often reproduced in computationally intensive simulations, such as Monte-Carlo simulations - MC and resampling methods, as is the case with bootstrap resampling.
 Statistics is just one example within so many other areas that need performance and uses the R language.
+-->
 
-In addition to the adoption of good programming practices and the maximum, efficient and adequate use of available computational resources, such as code parallelization, through multicore parallelism procedures allowed by most current processors and operating systems, small adjustments and linkage of libraries can provide useful benefits.
+<!-- In addition to the adoption of good programming practices and the maximum, efficient and adequate use of available computational resources, such as code parallelization, through multicore parallelism procedures allowed by most current processors and operating systems, small adjustments and linkage of libraries can provide useful benefits.
+-->
 
@@
 
-The `ropenblas` package can be installed in two ways.
+<!-- The `ropenblas` package can be installed in two ways.
 The first is using the `install.packages()` function of the `utils` package which is available in any basic language installation and the second is using the `devtools` package which will allow the package to be installed directly from the development directory on GitHub.
+-->
 
@@
 
-```{r bench, echo = FALSE, fig.cap = "Benchmarks of a decomposition of singular and inverse value of a matrix of dimension 1000 x 1000.", fig.align = "center", out.width="90%"}
+```{r bench, echo = FALSE, fig.cap = "Benchmarks of a decomposition of singular and inverse value of a matrix of dimension 1000 x 1000.", fig.align = "center", out.width="60%"}
 knitr::include_graphics(path = "benchmark.png") 

### 2021-03-19 paper/paper.Rmd
Update

@@
 The `ropenblas` package is already available on the Comprehensive R Archive Network - CRAN, currently in version 0.2.9, and the project is maintained on GitHub at <https://github.com/prdm0/ropenblas> where contributors can find other details of the code, information, as well as being able to contribute with the development of the project.
-Information can also be found on the project website.
-On the website, it is also possible to read the `NEWS.md` file with details of the versions and the focus of the current development.
+
+<!-- Information can also be found on the project website.  -->
+
+<!-- On the website, it is also possible to read the `NEWS.md` file with details of the versions and the focus of the current development.
 The site is deposited at <https://prdm0.github.io/ropenblas/>.
 Suggestions for improvements and bug reports can be sent via the link <https://github.com/prdm0/ropenblas/issues>.
-You can find out how to contribute to the package by accessing the `CONTRIBUTING.md` file at <https://github.com/prdm0/ropenblas/blob/master/CONTRIBUTING.md>.
+-->
+
+<!-- You can find out how to contribute to the package by accessing the `CONTRIBUTING.md` file at <https://github.com/prdm0/ropenblas/blob/master/CONTRIBUTING.md>. -->
 
@@
 
-The use of the function is quite simple, just by running the code `link_again()` since the function has no arguments.
+<!-- The use of the function is quite simple, just by running the code `link_again()` since the function has no arguments.
 It will automatically detect if there was a link break that will be rebuilt again without the need for any compilation.
@@
 Link breakage rarely occurs, but if it does, it can be resolved quickly.
-The following code and image exemplify a possible reconstruction of symbolic links using the `link_again()` function:
+The following code and image exemplify a possible reconstruction of symbolic links using the `link_again()` function: -->
 
-```{r, eval=FALSE, prompt=TRUE}
-link_again()
-```
+<!-- ```{r, eval=FALSE, prompt=TRUE} -->
+<!-- link_again() -->
+<!-- ``` -->
 

### 2021-03-22 paper/paper.Rmd
Update

--- 2021-03-11 paper/paper.Rmd
@@
 
-The `ropenblas` package aims to facilitate the day-to-day life of R programmers who want a little more performance on GNU/Linux systems, without removing the possibility that specific configurations are made, if they deem convenient.
+The `ropenblas` package aims to facilitate the day-to-day life of R programmers who want more performance on GNU/Linux systems, without removing the possibility that specific configurations are made, if they deem convenient, that is, more technical users will be able to pass other flags that will be considered in the compilation process.
 Through the package's `ropenblas()` and `rcompiler()` functions, the library user will be able to compile and link the R language in his GNU/Linux distribution with the OpenBLAS library, all within R and in a very simple fashion.
@@
 
-The `ropenblas` package aims to provide useful and simple experiences to R [@R] programmers who develop their activities on GNU/Linux operating systems, these many developers around the world producing codes of great impact for the community.
-These experiences consist of being able to link any version of the OpenBLAS [@openblas] library to the R language, as well as allowing the programmer to install and link various versions of R and make them available on his operating system as well as switch between these versions as they see fit.
+The `ropenblas` package aims to provide useful and simple experiences to R [@R] programmers who develop their activities on GNU/Linux operating systems.
+These experiences consist of being able to link any version of the OpenBLAS [@openblas] library to the R language, as well as allowing the programmer to install and link various versions of R and make them available on their operating system as well as switch between these versions as they see fit.
 
@@
 The `ropenblas` package is already available on the Comprehensive R Archive Network - CRAN, currently in version 0.2.9, and the project is maintained on GitHub at <https://github.com/prdm0/ropenblas> where contributors can find other details of the code, information, as well as being able to contribute with the development of the project.
-Information can also be found on the project website.
 On the website, it is also possible to read the `NEWS.md` file with details of the versions and the focus of the current development.
@@
 ```{r logo, echo = FALSE, message = FALSE, fig.cap = "Computer library logo.", fig.align = "center", out.width="30%"}
-
 knitr::include_graphics(path = "logo.png") 
-
 ```
@@
 
-<!-- The following subsections are intended to explain and exemplify the use of these functions focused on the main problems that can be solved using the `ropenblas` package.
-Some functions may take a few minutes to run, as they are responsible for compiling code that is considerably larges and complicateds.
-This is the case with the `rcompiler()` and  `ropenblas()` functions.
--->
-
-## 'last_version_r' function
-
-The function `last_version_r()` automatically searches, in the official repositories of language R, for information about versions of language R.
-Its general use is `last_version_r(major = NULL)`, where the argument major indicates which is the largest version of R that you want to search for the version list.
-Therefore, for argument `major`, a number must be passed, preferably an integer that indicates which is the largest version to be considered.
-
-<!-- Consider the example: -->
-
-<!-- ```{r packages, echo=FALSE, cache=TRUE} -->
-
-<!-- library("ropenblas") -->
-
-<!-- ``` -->
-
-<!-- ```{r, prompt=TRUE, dependson="ropenblas", cache=TRUE, eval=FALSE} -->
-
-<!-- last_version_r(major = 4L) -->
-
-<!-- ``` -->
-
-<!-- Note that the `last_version_r()` function returns a list of three elements, where the first element called `last_version` returns the latest version of the R language based on the argument `major`.
-Thus, the latest version of the R language since the largest version is $3$ is version $3.6.3$.
-The second element of name `versions` of the return list is a vector containing all versions of the language R for `major = 3L`.
-The third and last element of the return list is named `n` and returns an integer value referring to the number of versions of R given `major = 3L`.
-By default, the `major` argument of the `last_version_r()` function is `NULL`.
--->
-
-<!-- Considering the standard, the function will always consider the largest current version of the language, as in the example below: -->
-
-<!-- ```{r, dependson="ropenblas", cache=TRUE, prompt=TRUE} -->
-
-<!-- last_version_r(major = NULL) -->
-
-<!-- ``` -->
-
-<!-- The function is always adapted to search for new versions and will understand the new language updates since it has been implemented in a general way.
-Therefore, `last_version_r(major = NULL)$last_version` will always return the latest version of R and not the latest version of R available in the repositories of your GNU/Linux distribution.
-Therefore, it may be that, depending on when this function is performed, different results may occur.
--->
-
-## 'last_version_openblas' function
-
-The `last_version_openblas()` function works similarly to the `last_version_r()` function, returning a list of three elements named in the same way with the information from the latest version, all the versions, and the number of versions of the OpenBLAS library, respectively.
-
-<!-- Unlike the `last_version_r()` function that searches for the versions of R on the official language website, the `last_version_openblas()` function will search for information on the OpenBLAS library versions on official language development repository on GitHub.
-In addition, due to the way that the versions of the OpenBLAS library are numbered, the function will always consider the universe of all versions of the OpenBLAS library, therefore, being a function without arguments.
-The latest version of the OpenBLAS library can be returned by doing `last_version_openblas()$last_version`.
-Just like the `last_version_r()` function, the `last_version_openblas()` function does not depend on which version of OpenBLAS is available in the repositories of your GNU/Linux distribution.
--->
-
-<!-- ```{r, dependson="ropenblas", cache=TRUE, prompt=TRUE} -->
-
-<!-- last_version_openblas() -->
-
-<!-- ``` -->
-
-## 'rcompiler' function
-
-This function is responsible for compiling a version of the R language.
-The x argument is the version of R that you want to compile.
-For example, `x = "4.0.4"` will compile and link the R-4.0.4 version as the major version on your system.
-By default (`x = NULL`) will be compiled the latest stable version of the R.
-For example, to compile the latest stable version of the R language, run `rcompiler()`.
-The `rcompiler()` function can only be used if the user is an administrator of the GNU/Linux distribution.
-If the user is using programming IDE's, a screen similar to the image below will be displayed requesting the entry of the system administrator password.
-
-<!-- ```{r, echo=FALSE, message=FALSE, warning=FALSE, fig.align='center', fig.cap="Window for entering the system administration password.", out.width="55%"} -->
-
-<!-- knitr::include_graphics("root.png") -->
-
-<!-- ``` -->
-
-<!-- If the user is running the R language in a terminal of the GNU/Linux distribution, a Shell Bash type terminal, they will be asked to include the password by the terminal itself.
-The function will not change the operation of other programs, nor even major changes will be made in the initial version of R, just summarizing the creation of symbolic links.
--->
-
-<!-- The general way of using the function is given by: -->
-
-<!-- **General use**: -->
-
-```{r, eval=FALSE, prompt=TRUE}
-rcompiler(x = NULL, with_blas = NULL, complementary_flags = NULL)
-```
-
-<!-- The function's arguments are described below: -->
-
--   `x`: String with a valid R language version.
-A list valid of the latest language versions can be obtained using the `last_version_r()` function.
-You can move to `x` any of the returned versions.
-This is the best way to choose a valid argument for `x`.
-By default, `x = NULL` is equivalent to pass `last_version_r()$last_version`, that is, it will be considered the last stable version of the R language;
--   `with_blas`: This argument sets the `--with-blas` flag in the R language compilation process and must be passed as a string. Details on the use of this flag can be found here;
--   `complementary_flags`: String with complementary flags to be used in the R language compilation process.
-
-If the goal is to install the R language, switch between versions of R, and link the installed versions of the language with the OpenBLAS library, you shouldn't have to worry about the `with_blas` and `complementary_flags` arguments, respectively.
-For more details, consult the `README.md` of the project or the official documentation of the package in [CRAN](https://cran.r-project.org/web/packages/ropenblas/ropenblas.pdf).
-
-<!-- These arguments are useful for a minority of programmers who feel very specific needs to pass complementary flags to be considered in the R language compilation process, the inclusion of complementary library directories, among other arguments that can be found in the official language manuals.
-By default, if nothing is passed to the `with_blas` and `complementary_flags` arguments, the compilation will be performed as follows: -->
-
-<!-- ```{bash, eval=FALSE} -->
-
-<!-- ./configure --prefix=/opt/R/version_r --enable-memory-profiling -->
-
-<!-- --enable-R-shlib --enable-threads=posix -->
-
-<!-- --with-blas="-L/opt/OpenBLAS/lib -I/opt/OpenBLAS/include -lpthread -lm" -->
-
-<!-- ``` -->
-
-<!-- As a suggestion and if you want to use the complementary arguments, that is, use `with_blas` and `complementary_flags`, do not change the directory `include` and `lib` of the OpenBLAS library in argument `with_blas`, considering that the `rcompiler()` function will always install the OpenBLAS library in the `/opt/OpenBLAS` directory, thus avoiding problems with breaking important links on your system and in the configuration of the initial version of R.
-If you try to pass a different installation directory to the OpenBLAS library, the `rcompiler()` function will disregard this installation of OpenBLAS and perform a safe installation in the `/opt/OpenBLAS` directory.
-Everything is built in this directory and symbolic links are used so that the initial state of R configuration in the GNU/Linux distribution is not changed.
-This allows no errors to be made and unforeseen bugs to occur.
-If there are reasons to consider complementary strings for the arguments `with_blas` and `complementary_flags`, the R language will be compiled as follows: -->
-
-<!-- ```{bash, eval=FALSE} -->
-
-<!-- --prefix=/opt/R/version_r --enable-memory-profiling --enable-R-shlib -->
-
-<!-- --enable-threads=posix --with-blas="..." complementary_flags -->
-
-<!-- ``` -->
-
-<!-- Although the initial description of the `rcompiler()` function may seem a little complicated, its use is very simple.
-Below I will exemplify some situations in which the use of the `rcompiler()` function may be convenient.
--->
-
-<!-- **Example**: In the hypothetical situation of an R user on any GNU/Linux distribution, if are interested in knowing the latest version of the R language, installing it and linking it to the OpenBLAS library, it should proceed as follows: -->
-
-<!-- ```{r, eval=FALSE, prompt=TRUE} -->
-
-<!-- rcompiler(x = "4.0.2") # or simply rcompiler () or rcompiler (x = NULL) -->
-
-<!-- ``` -->
-
-<!-- After executing the function, everything will be ready, and can be checked by executing the command `extSoftVersion()["BLAS"]` in the next execution of R, that is, in a new instance.
-Thus the user will know that the compilation of the R library, and if necessary, of the OpenBLAS library was carried out as requested.
-Briefly, the `extSoftVersion()["BLAS"]` command will return something like: -->
-
-<!-- ```{r, prompt=TRUE} -->
-
-<!-- extSoftVersion()["BLAS"] -->
-
-<!-- ``` -->
-
-<!-- ```{r, prompt=TRUE} -->
-
-<!-- sessionInfo() -->
-
-<!-- ``` -->
-
-<!-- **Example**: In a new hypothetical situation of a user of R having installed two different versions of the R language as presented above, using the function `rcompiler()`, for example, versions 3.6.3 and 4.0.0, so: -->
-
-<!-- ```{r, eval=FALSE, prompt=TRUE} -->
-
-<!-- # First installation of R performed by the rcompiler() function: -->
-
-<!-- rcompiler(x = "4.0.0")  -->
-
-<!-- # Second installation of R performed by the rcompiler() function: -->
-
-<!-- rcompiler(x = "3.6.3") -->
-
-<!-- # Returning version 4.0.0 from R: -->
-
-<!-- rcompiler(x = "4.0.0") -->
-
-<!-- ``` -->
-
-<!-- Running the code `rcompiler(x = "4.0.0")` as the last line of the example above will allow the user to link the binaries previously created in the 4.0.0 compilation process when `rcompiler(x = "4.0.0")` was run for the first time.
-This will avoid a compilation so that switching between versions of R that have already been compiled will be quick and easy.
-Although this seems ideal and it is, the function will ask if the user wants to recompile an already compiled version.
--->
-
-<!-- **Example**: Assuming that the user of the package has already used the function `rcompiler(x = "4.0.0")` and is in a version other than 4.0.0 but intends to return to version 4.0.0, he can return without compile the language again, as shown in the image below.
-The output was placed in the form of an image since the return of the functions of the package use symbols that facilitate the user of the functions of the package to understand the suggestions, as well as understand if something went right or wrong.
--->
-
-<!-- ```{r, eval=FALSE} -->
-
-<!-- rcompiler(x = "4.0.0") -->
-
-<!-- ``` -->
-
-<!-- ```{r, echo=FALSE, message=FALSE, warning=FALSE, fig.align='center', fig.cap="A possible exit from the 'rcompiler' function.
-Suggestion of switching between versions of R without the need to recompile the language.", out.width="100%"} -->
-
-<!-- knitr::include_graphics("linkar_again.png") -->
-
-<!-- ``` -->
-
-<!-- Due to the internal dependencies of the `ropenblas` package, it is advisable not to try to go to versions of R prior to 3.1.0, as these dependencies do not work on these versions of R.
-Therefore, in earlier versions of R, installing the `ropenblas` package will not be possible.
-Therefore, if the user wishes to return to a more current version of R, he must install the language R in the GNU/Linux distribution without the help of the package.
-Although it is allowed to install previous versions of R prior to 3.1.0, it will only be done after the user responds to some questions of an alert message, as shown in the image below: -->
-
-<!-- ```{r, eval=FALSE, prompt=FALSE} -->
-
-<!-- rcompiler(x = "3.0.0") -->
-
-<!-- ``` -->
-
-<!-- ```{r, echo=FALSE, message=FALSE, warning=FALSE, fig.align='center', fig.cap="Attempted to install an R language version prior to version 3.1.0.", out.width="100%"} -->
-
-<!-- knitr::include_graphics("attention.png") -->
-
-<!-- ``` -->
-
-## 'ropenblas' function
-
-The `ropenblas()` function, a function of the same name in the package, links the main version of the R language installed on your operating system with the OpenBLAS library.
-As in the `rcompiler()` function, the `ropenblas()` function requires the operating system administration password, that is, it must be executed by the system administrator.
-
-<!-- Unlike the `rcompiler()` function that will allow multiple versions of R to be available in your GNU/Linux distribution, the `ropenblas()` function will allow only one version of the OpenBLAS library to be installed.
-The function will allow versions of OpenBLAS $\geq 0.3.0$ to be installed.
-Even if the function `rcompile()` responsible for compiling and installing the R language has not been used, the function `ropenblas()` may link a version of OpenBLAS to the main installation of R, that is, even if the R is installed by procedures external to the package.
--->
-
-<!-- **General use**: -->
-
-```{r, eval = FALSE, prompt=TRUE}
-ropenblas(x = NULL, restart_r = TRUE)
-```
-
-The `ropenblas()` function is made up of two arguments. Are they:
-
--   `x`: String with the version of the OpenBLAS library to be compiled, installed, and linked with the main R installation (by default it is considered the latest version);
--   `restart_r`: Logical value (default `restart_r = TRUE`) to update the R section after compiling, installing, and linking the OpenBLAS library.
-
-<!-- By default, if `x = NULL` the latest version of the OpenBLAS library will be considered.
-This is equivalent to passing `last_version_openblas()$last_version` to `x`.
-There are no great reasons to consider an older version of the OpenBLAS library, although the `ropenblas` package will allow this to be done in a simple way, as in the following example:  -->
-
-<!-- **Example**: Regardless of how the R language was installed, suppose you want to compile, install and link the latest version of the OpenBLAS library to the R language.
-This can be done by doing: -->
-
-<!-- ```{r, eval=FALSE, prompt=TRUE} -->
-
-<!-- ropenblas() -->
-
-<!-- ``` -->
-
-<!-- ```{r, echo=FALSE, message=FALSE, warning=FALSE, fig.align='center', fig.cap="Output informing the end of the procedure for linking the OpenBLAS library to the R language.", out.width="100%"} -->
-
-<!-- knitr::include_graphics("ropenblas_01.png") -->
-
-<!-- ``` -->
-
-<!-- **Example**: In situations where the latest version of the OpenBLAS library is already installed, if the user wishes to install a previous version of OpenBLAS, for example the version $0.3.8$, he should make it clear by answering a question, as shown in the image below: -->
-
-<!-- ```{r, eval=FALSE, prompt=TRUE} -->
-
-<!-- ropenblas("0.3.8") -->
-
-<!-- ``` -->
-
-<!-- ```{r, echo=FALSE, message=FALSE, warning=FALSE, fig.align='center', fig.cap="Asking if the user really wants to compile and link an older version of the OpenBLAS library.", out.width="100%"} -->
-
-<!-- knitr::include_graphics("ropenblas_02.png") -->
-
-<!-- ``` -->
-
 Table 1 below presents the benefit of considering an optimized version of BLAS.
@@
 
-\
-
 | Functions  | Library  | Time (seconds) |
-|----------- |----------|:---------------:|
+|------------|----------|:--------------:|
 | `svd(x)`   | BLAS     |     6.520      |
@@
 | `solve(x)` | OpenBLAS |     0.640      |
+
 : Comparison of the computational costs of the `svd()` and `solve()` functions (average of 100 repetitions).
@@
 
-```{r bench, echo = FALSE, fig.cap = "Benchmarks of a decomposition of singular and inverse value of a matrix of dimension 1000 x 1000.", fig.align = "center", out.width="90%"}
+```{r bench, echo = FALSE, fig.cap = "Benchmarks of a decomposition of singular and inverse value of a matrix of dimension 1000 x 1000.", fig.align = "center", out.width="65%"}
 knitr::include_graphics(path = "benchmark.png") 
@@
 
-## 'link_again' function
+<!-- ## 'link_again' function -->
 
-The `link_again()` function links again the OpenBLAS library with the R language, being useful to correct problems of untying the OpenBLAS library that is common when the operating system is updated.
+<!-- The `link_again()` function links again the OpenBLAS library with the R language, being useful to correct problems of untying the OpenBLAS library that is common when the operating system is updated.
 The function can link again the R language with the OpenBLAS library.
+-->
 
-Thus, `link_again()` will only make the linkage when in some previous section of R the `ropenblas()` function has been used for the initial binding of the R language with the OpenBLAS library.
+<!-- Thus, `link_again()` will only make the linkage when in some previous section of R the `ropenblas()` function has been used for the initial binding of the R language with the OpenBLAS library.
+-->
 
-The use of the function is quite simple, just by running the code `link_again()` since the function has no arguments.
+<!-- The use of the function is quite simple, just by running the code `link_again()` since the function has no arguments.
 It will automatically detect if there was a link break that will be rebuilt again without the need for any compilation.
@@
 Link breakage rarely occurs, but if it does, it can be resolved quickly.
-The following code and image exemplify a possible reconstruction of symbolic links using the `link_again()` function:
+The following code and image exemplify a possible reconstruction of symbolic links using the `link_again()` function: -->
 
-```{r, eval=FALSE, prompt=TRUE}
-link_again()
-```
+<!-- ```{r, eval=FALSE, prompt=TRUE} -->
+
+<!-- link_again() -->
+
+<!-- ``` -->
 
@@
 
-## 'rnews function'
+<!-- ## 'rnews function' -->
 
-The `rnews()` function returns the contents of the `NEWS.html` file in the standard browser installed on the operating system.
+<!-- The `rnews()` function returns the contents of the `NEWS.html` file in the standard browser installed on the operating system.
 The `NEWS.html` file contains the main changes from the recently released versions of the R language.
 The goal is to facilitate the query by invoking it directly from the R command prompt.
+-->
 

### 2021-03-22 paper/paper.Rmd
Update

@@
 
-```{r bench, echo = FALSE, fig.cap = "Benchmarks of a decomposition of singular and inverse value of a matrix of dimension 1000 x 1000.", fig.align = "center", out.width="65%"}
+```{r bench, echo = FALSE, fig.cap = "Benchmarks of a decomposition of singular and inverse value of a matrix of dimension 1000 x 1000.", fig.align = "center", out.width="60%"}
 knitr::include_graphics(path = "benchmark.png") 

### 2021-03-22 paper/paper.Rmd
Update

@@
 
-```{r bench, echo = FALSE, fig.cap = "Benchmarks of a decomposition of singular and inverse value of a matrix of dimension 1000 x 1000.", fig.align = "center", out.width="60%"}
+```{r bench, echo = FALSE, fig.cap = "Benchmarks of a decomposition of singular and inverse value of a matrix of dimension 1000 x 1000.", fig.align = "center", out.width="50%"}
 knitr::include_graphics(path = "benchmark.png") 

### 2021-03-30 paper/paper.Rmd
Update paper. Accepting suggestions from Avatar Kristen Thyng.

@@
 
-The `ropenblas` package aims to facilitate the day-to-day life of R programmers who want more performance on GNU/Linux systems, without removing the possibility that specific configurations are made, if they deem convenient, that is, more technical users will be able to pass other flags that will be considered in the compilation process.
+<!-- The `ropenblas` package aims to facilitate the day-to-day life of R programmers who want more performance on GNU/Linux systems, without removing the possibility that specific configurations are made, if they deem convenient, that is, more technical users will be able to pass other flags that will be considered in the compilation process.
 Through the package's `ropenblas()` and `rcompiler()` functions, the library user will be able to compile and link the R language in his GNU/Linux distribution with the OpenBLAS library, all within R and in a very simple fashion.
@@
 Linking the OpenBLAS library to R will bring better computational performance to the language in the most diverse algebraic operations commonly used in areas such as statistics, data science, and machine learning.
+-->
+
+The `ropenblas` package provides improved performance on GNU/Linux systems and allows for passing additional compilation flags for more technical users.
+Through the `ropenblas()` and `rcompiler()` functions, the user will be able to compile and link the GNU/Linux distribution R language with the OpenBLAS library, all within R and in a very simple fashion.
+It works for all GNU/Linux distributions.
+Linking the OpenBLAS library to R brings better computational performance to the language in the most diverse algebraic operations commonly used in areas such as statistics, data science, and machine learning.
 
@@
 
-The term "computational efficiency" is very common for those who program statistical methods, in which a large part of them involve algebraic operations that are often reproduced in computationally intensive simulations, such as Monte-Carlo simulations - MC and resampling methods, as is the case with bootstrap resampling.
+<!-- The term "computational efficiency" is very common for those who program statistical methods, in which a large part of them involve algebraic operations that are often reproduced in computationally intensive simulations, such as Monte-Carlo simulations - MC and resampling methods, as is the case with bootstrap resampling.
 Statistics is just one example within so many other areas that need performance and uses the R language.
+-->
+
+Computational efficiency is important for those who program statistical methods since they often involve algebraic operations reproduced in computationally intensive simulations, such as Monte-Carlo simulations and resampling methods, as is the case with bootstrap resampling.
+Statistics is just one example within other areas that need good performance and use the R language.
 
@@
 
-The `ropenblas` package aims to provide useful and simple experiences to R [@R] programmers who develop their activities on GNU/Linux operating systems.
+<!-- The `ropenblas` package aims to provide useful and simple experiences to R [@R] programmers who develop their activities on GNU/Linux operating systems.
 These experiences consist of being able to link any version of the OpenBLAS [@openblas] library to the R language, as well as allowing the programmer to install and link various versions of R and make them available on their operating system as well as switch between these versions as they see fit.
+-->
+
+The `ropenblas` package aims to be easy to use for R [@R] programmers who work on GNU/Linux operating systems.
+For example, a user can link any version of the OpenBLAS [@openblas] library to the R language and install and link various versions of R to make them available on their operating system as well as switch between these versions.
 

### 2021-03-31 README.Rmd
Update README.md. Add DOI of the paper.

@@
   |
+  | **Package website**: **<https://prdm0.github.io/ropenblas>**
+  |
   | **Summary**
-  | **Package website**: **<https://prdm0.github.io/ropenblas>**
 output: 
   bookdown::github_document2:
-    number_sections: true
+    number_sections: false
     toc: true
@@
 
-**ropenblas**
+**ropenblas package**
 
+[![DOI](https://joss.theoj.org/papers/10.21105/joss.02769/status.svg)](https://doi.org/10.21105/joss.02769)
 [![last](https://www.r-pkg.org/badges/last-release/ropenblas)](https://CRAN.R-project.org/package=ropenblas)

### 2021-04-06 img/logo/creating_logo.R
:art: Update of the logo and code that generates the logo
Hex Logo update and code update for automatic logo generation.

@@ -1,8 +1,40 @@
-# remotes::install_github("GuangchuangYu/hexSticker")
+# remotes::install_github("GuangchuangYu/hexSticker", force = TRUE)
 
 library(hexSticker)
+library(ggplot2)
+library(glue)
+library(magick)
+library(fs)
 
-imgurl <- system.file("~/Downloads/ropenblas/inst/openblas_logo_01.png", package="hexSticker")
+img <- image_read(path(getwd(), "img", "logo", "img.png"))
+logo <- image_ggplot(img, interpolate = TRUE)
 
-sticker("~/Downloads/ropenblas/inst/logo/molde.png", package="", p_size=22, s_x=1.03, s_y=.95, s_width=1,
-        filename="openblas_logo.png", h_fill="#000000", h_color="#929292", white_around_sticker = T)
+s <- sticker(
+  logo,
+  package = "ropenblas",
+  p_size = 20,
+  s_width = 1.3,
+  s_height = 1.3,
+  s_x = 1.1,
+  s_y = 0.84,
+  h_fill = "#FE5750",
+  h_color = "#E8DF9C",
+  p_color = "#0F2536",
+  p_family = "Aller_Rg",
+  h_size = 2,
+  white_around_sticker = T,
+  filename = path(getwd(), "img", "logo", "logo.png"),
+  url = "https://prdm0.github.io/ropenblas/",
+  u_size = 4.5,
+  spotlight = T,
+  l_alpha = 0.4,
+  dpi = 300,
+  u_color = "white"
+)
+
+fs::file_delete(fs::path(getwd(), "logo.png"))
+
+fs::file_copy(
+  path = path(getwd(), "img", "logo", "logo.png"),
+  new_path = path(getwd(), "logo.png")
+)

### 2021-04-06 img/logo/creating_logo.R
:art: Update website
Update website (pkgdown)

@@ -17,7 +17,7 @@ s <- sticker(
   s_height = 1.3,
   s_x = 1.1,
   s_y = 0.84,
-  h_fill = "#FE5750",
+  h_fill =  "#FE5750",
   h_color = "#E8DF9C",
   p_color = "#0F2536",
   p_family = "Aller_Rg",
@@ -27,7 +27,7 @@ s <- sticker(
   url = "https://prdm0.github.io/ropenblas/",
   u_size = 4.5,
   spotlight = T,
-  l_alpha = 0.4,
+  l_alpha = 0.3,
   dpi = 300,
   u_color = "white"
 )

### 2021-04-06 README.Rmd
:art: Update logo and website
Update logo (logo with transparent background) and pkgdown.

@@
 
-```{r, fig.align='center', echo=FALSE, out.width=219}
-knitr::include_graphics("https://raw.githubusercontent.com/prdm0/ropenblas/master/logo.png")
-```
+<!-- ```{r, fig.align='center', echo=FALSE, out.width=219} -->
+<!-- knitr::include_graphics("https://raw.githubusercontent.com/prdm0/ropenblas/master/logo.png") -->
+<!-- ``` -->
 
-<!-- <img src="https://raw.githubusercontent.com/prdm0/ropenblas/master/logo.png" height="270" width="250" align="right" /> -->
+<img src="logo.png" height="230" width="200" align="right" />
 

### 2021-04-06 img/logo/creating_logo.R

@@ -9,7 +9,7 @@ library(fs)
 img <- image_read(path(getwd(), "img", "logo", "img.png"))
 logo <- image_ggplot(img, interpolate = TRUE)
 
-s <- sticker(
+sticker(
   logo,
   package = "ropenblas",
   p_size = 20,
@@ -29,7 +29,7 @@ s <- sticker(
   spotlight = T,
   l_alpha = 0.3,
   dpi = 300,
-  u_color = "white"
+  u_color = "#85dfce"
 )
 
 fs::file_delete(fs::path(getwd(), "logo.png"))

### 2021-04-14 README.Rmd
Add .travis.yml (Travis CI).

@@
 [![DOI](https://joss.theoj.org/papers/10.21105/joss.02769/status.svg)](https://doi.org/10.21105/joss.02769)
+[![Travis build status](https://travis-ci.com/prdm0/ropenblas.svg?branch=master)](https://travis-ci.com/prdm0/ropenblas)
 [![last](https://www.r-pkg.org/badges/last-release/ropenblas)](https://CRAN.R-project.org/package=ropenblas)
